### 2023-02-28 paper/main.tex
Added framework for paper

\documentclass[letterpaper, 10 pt, conference]{ieeeconf} 
\IEEEoverridecommandlockouts                              
\overrideIEEEmargins

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{graphicx}

\begin{document}

\thispagestyle{empty}
\pagestyle{empty}

\input{titlepage}
%%%%%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\end{abstract}

%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Problem Definition}

\section{Application Benefits}

\section{Requirements Elicitation and Specification}

\section{Top-level and Low-level Software Design}

\section{Software Construction}

\section{Technical Documentation}

\section{Acceptance Testing}

\section{Conclusion}

\addtolength{\textheight}{-12cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}

Appendixes should appear before the acknowledgment.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.

\begin{thebibliography}{99}

\bibitem{young-1964} G. O. Young, Synthetic structure of industrial plastics (Book style with paper title and editor), 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
\bibitem{chen-1993} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
\bibitem{poor-1985} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.

\bibitem{uofr} "Home", University of Regina, 2022. [Online]. Available: https://www.uregina.ca/. [Accessed: 06- Apr- 2022].

\end{thebibliography}

\end{document}

### 2023-02-28 paper/main.tex
updated main.tex to include info from proposal

@@
 \section{Problem Definition}
+Develop a software that facilitates administration of surveys and feedback collection. The software must be fast, robust, and friendly.
+
+Marketing/Business Operations
+
+Businesses want meaningful direct feedback on their products and services.
+Our project aims to provide a generalized solution to context-specific customer feedback monitoring without the need of onsite hardware to capture responses.
+In other terms, our app is a solution for conducting self-administered surveys.
+
+Our application is a simple tool for conducting self-administered surveys.
+Our users can log into their profiles to view customer feedback to improve their businesses.
+QR codes can be generated for wide distribution and quick access.
+SurveyMonkey (https://www.surveymonkey.com/) and QuestionPro (https://www.questionpro.com/) are comparable existing systems.
+Some benefits of our application are that the users can received unlimited number of responses for their surveys without cost and all features to create the surveys are free as well.
+Our application does not have many templates and complicated tools that may negatively impact loading time.
+Respondents do not need to create an account to respond to surveys.
 
@@
 \section{Requirements Elicitation and Specification}
+Two types of users/roles: Feedback Gatherer / Respondent.
+
+\textbf{Feedback Gatherer}
+
+    Register: Feedback gatherer creates an account by entering the required information
+
+    Create Survey: Feedback gatherer creates a survey by entering questions and selecting type of responses
+
+    View QR Code: Feedback gatherer views the generated QR code for the survey
+
+    Delete Survey: Feedback gatherer deletes a survey that is no longer required
+
+    View Statistics and responses: Feedback gatherer views statistics and responses of a selected survey
+
+\textbf{Respondent}
+
+    Scan QR Code: Respondent scans the QR code to view the survey
+
+    Enter responses: Respondent enters responses to the survey questions
+
+    Submit: Respondent submits responses to the survey questions
+
+The feedback gatherer can create a survey after registering.
+The feedback gatherer has the option to delete an existing survey or view statistics and responses to an existing survey.
+After creating a survey, the feedback gatherer can view the QR code to administer the created survey.
+
+The respondent can scan the QR code to take a survey created by a feedback gatherer. The respondent enters responses to the survey and submit the responses.
 

### 2023-03-05 paper/main.tex
updated files for the paper
formatting for title page and description of requirements for main body

@@
 \section{Problem Definition}
+\subsection{outline the problem requirements and include the ap- plication domain and motivations of your project (1 page).}
 Develop a software that facilitates administration of surveys and feedback collection. The software must be fast, robust, and friendly.
@@
 \section{Application Benefits}
+\subsection{what are the benefits of your application when compared to existing systems. Choose two systems only and include their references (2 pages).}
 
 \section{Requirements Elicitation and Specification}
+\subsection{Functional requirements list (only the ones that you have imple- mented) for each user role (two exactly). Name each requirement and explain it briefly.}
+\subsection{For each user role, provide the use case diagram with all the use cases and actors.}
+\subsection{Describe in detail two use cases using the activity diagram. Choose the most complex use cases.}
+\subsection{Software qualities: Correctness, Time-eﬀiciency and Robustness.
+In- clude at least two concrete examples for each quality for each user role.
+The sign-in and sign-up use cases are excluded from the examples.
+}
+
 Two types of users/roles: Feedback Gatherer / Respondent.
@@
 \section{Top-level and Low-level Software Design}
+\subsection{Provide the MVC architecture according to the selected Web frame- work. Also, describe at least three benefits of MVC for your application.}
+\subsection{Observer and Factory design patterns.
+Explain in detail the usability of these two patterns for your specific application.
+Include the complete class diagram for each pattern.
+Also provide the algorithms corresponding to the pattern’s important methods.
+For each class, provide the data types of the attributes and prototypes of the methods.}
+\subsection{Provide the class diagram of the whole system by incorporating the two design patterns.
+}
 
 \section{Software Construction}
+\subsection{Submit the screenshot of the entire structure of the code within the web framework.}
+\subsection{Deployment diagram regarding the hardware configuration of the code. Indicate the supported Web browsers, the application/Web servers and the database solution.}
+\subsection{Screenshots of all table contents of the system data.}
+\subsection{GitHub link of the entire program.
+All students must contribute equally to the programming part.
+The commit log of each student will be checked within GitHub.
+Website builders, such as Wordpress, are not allowed.}
+\subsection{Link of your Web-based application. The application should be acces- sible online and runnable.}
 
 \section{Technical Documentation}
+\subsection{List of programming languages.}
+\subsection{List of reused algorithms and programs. Include their sources.}
+\subsection{List of software tools and environments. Provide briefly their benefits specifically for your application.}
 
-\section{Acceptance Testing}
+\section{Acceptance Testing: select test cases for both user roles. The sign-in and sign-up are excluded from testing.}
+\subsection{Correctness testing using four test cases (screenshots of both inputs and out- puts).}
+\subsection{Robustness testing using four test cases (screenshots of both inputs and out- puts).}
+\subsection{Time-eﬀiciency testing of two functions (with screenshots). Indicate the method you used to measure the time.}
 

### 2023-03-06 django/CS476P/CS476P/CS476P/asgi.py
added form editor JS files and unzipped the zip

@@ -1,0 +1,16 @@
+"""
+ASGI config for CS476P project.
+
+It exposes the ASGI callable as a module-level variable named ``application``.
+
+For more information on this file, see
+https://docs.djangoproject.com/en/4.1/howto/deployment/asgi/
+"""
+
+import os
+
+from django.core.asgi import get_asgi_application
+
+os.environ.setdefault('DJANGO_SETTINGS_MODULE', 'CS476P.settings')
+
+application = get_asgi_application()

### 2023-03-06 django/CS476P/CS476P/CS476P/settings.py

@@ -1,0 +1,142 @@
+"""
+Django settings for CS476P project.
+
+Generated by 'django-admin startproject' using Django 4.1.7.
+
+For more information on this file, see
+https://docs.djangoproject.com/en/4.1/topics/settings/
+
+For the full list of settings and their values, see
+https://docs.djangoproject.com/en/4.1/ref/settings/
+"""
+
+from pathlib import Path
+import os
+
+# Build paths inside the project like this: BASE_DIR / 'subdir'.
+BASE_DIR = Path(__file__).resolve().parent.parent
+
+
+# Quick-start development settings - unsuitable for production
+# See https://docs.djangoproject.com/en/4.1/howto/deployment/checklist/
+
+# SECURITY WARNING: keep the secret key used in production secret!
+SECRET_KEY = 'django-insecure-m$!7d!!7*kf3#ii&w9*6pk%-6i62#%ngn1fic6iz$3!(^m_ud%'
+
+# SECURITY WARNING: don't run with debug turned on in production!
+DEBUG = True
+
+ALLOWED_HOSTS = ['localhost', '127.0.0.1']
+
+
+# Application definition
+
+INSTALLED_APPS = [
+    'django.contrib.admin',
+    'django.contrib.auth',
+    'django.contrib.contenttypes',
+    'django.contrib.sessions',
+    'django.contrib.messages',
+    'django.contrib.staticfiles',
+
+    'projects.apps.ProjectsConfig',
+    'users.apps.UsersConfig',
+]
+
+MIDDLEWARE = [
+    'django.middleware.security.SecurityMiddleware',
+
+    'whitenoise.middleware.WhiteNoiseMiddleware',
+
+    'django.contrib.sessions.middleware.SessionMiddleware',
+    'django.middleware.common.CommonMiddleware',
+    'django.middleware.csrf.CsrfViewMiddleware',
+    'django.contrib.auth.middleware.AuthenticationMiddleware',
+    'django.contrib.messages.middleware.MessageMiddleware',
+    'django.middleware.clickjacking.XFrameOptionsMiddleware',
+]
+
+ROOT_URLCONF = 'CS476P.urls'
+
+TEMPLATES = [
+    {
+        'BACKEND': 'django.template.backends.django.DjangoTemplates',
+        'DIRS': [
+            os.path.join(BASE_DIR, 'templates'),
+        ],
+        'APP_DIRS': True,
+        'OPTIONS': {
[…]

### 2023-03-06 django/CS476P/CS476P/CS476P/urls.py

@@ -1,0 +1,30 @@
+"""CS476P URL Configuration
+
+The `urlpatterns` list routes URLs to views. For more information please see:
+    https://docs.djangoproject.com/en/4.1/topics/http/urls/
+Examples:
+Function views
+    1. Add an import:  from my_app import views
+    2. Add a URL to urlpatterns:  path('', views.home, name='home')
+Class-based views
+    1. Add an import:  from other_app.views import Home
+    2. Add a URL to urlpatterns:  path('', Home.as_view(), name='home')
+Including another URLconf
+    1. Import the include() function: from django.urls import include, path
+    2. Add a URL to urlpatterns:  path('blog/', include('blog.urls'))
+"""
+from django.contrib import admin
+from django.urls import path, include
+
+
+from django.conf import settings
+from django.conf.urls.static import static
+
+urlpatterns = [
+    path('admin/', admin.site.urls),
+    path('', include('projects.urls')),
+    path('users/', include('users.urls')),
+]
+
+urlpatterns += static(settings.MEDIA_URL, document_root=settings.MEDIA_ROOT)
+urlpatterns += static(settings.STATIC_URL, document_root=settings.STATIC_ROOT)

### 2023-03-06 django/CS476P/CS476P/CS476P/wsgi.py

@@ -1,0 +1,16 @@
+"""
+WSGI config for CS476P project.
+
+It exposes the WSGI callable as a module-level variable named ``application``.
+
+For more information on this file, see
+https://docs.djangoproject.com/en/4.1/howto/deployment/wsgi/
+"""
+
+import os
+
+from django.core.wsgi import get_wsgi_application
+
+os.environ.setdefault('DJANGO_SETTINGS_MODULE', 'CS476P.settings')
+
+application = get_wsgi_application()

### 2023-03-06 django/CS476P/CS476P/projects/migrations/0003_form_project_featured_image_response.py

@@ -1,0 +1,38 @@
+# Generated by Django 4.1.7 on 2023-03-02 00:59
+
+from django.db import migrations, models
+import django.db.models.deletion
+import uuid
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('projects', '0002_tag_project_vote_ratio_project_vote_total_review_and_more'),
+    ]
+
+    operations = [
+        migrations.CreateModel(
+            name='Form',
+            fields=[
+                ('id', models.UUIDField(default=uuid.uuid4, editable=False, primary_key=True, serialize=False, unique=True)),
+                ('created', models.DateTimeField(auto_now_add=True)),
+                ('title', models.CharField(max_length=200)),
+                ('description', models.TextField(blank=True, null=True)),
+            ],
+        ),
+        migrations.AddField(
+            model_name='project',
+            name='featured_image',
+            field=models.ImageField(blank=True, default='default.jpg', null=True, upload_to=''),
+        ),
+        migrations.CreateModel(
+            name='Response',
+            fields=[
+                ('id', models.UUIDField(default=uuid.uuid4, editable=False, primary_key=True, serialize=False, unique=True)),
+                ('created', models.DateTimeField(auto_now_add=True)),
+                ('response_text', models.TextField(blank=True, null=True)),
+                ('form', models.ForeignKey(on_delete=django.db.models.deletion.CASCADE, to='projects.form')),
+            ],
+        ),
+    ]

### 2023-03-06 django/CS476P/CS476P/projects/urls.py

@@ -1,0 +1,14 @@
+from django.urls import path
+from . import views
+
+urlpatterns = [
+    path('', views.home, name="home"),
+    path('createsurvey/', views.createsurvey, name="createsurvey"),
+    path('landingpage/', views.landingpage, name="landingpage"),
+    path('login/', views.login, name="login"),
+    path('profile/', views.profile, name="profile"),
+    path('QRcode/', views.QRcode, name="QRcode"),
+    path('signup/', views.signup, name="signup"),
+    path('survey/', views.survey, name="survey"),
+    path('thanks/', views.thanks, name="thanks"),
+]

### 2023-03-06 django/CS476P/CS476P/users/models.py

@@ -1,0 +1,34 @@
+from django.db import models
+from django.contrib.auth.models import User
+import uuid
+
+# Create your models here.
+
+class Profile(models.Model):
+    user = models.OneToOneField(User, on_delete=models.CASCADE,null=True,blank=True)
+    name = models.CharField(max_length=200,blank=True,null=True)
+    email = models.EmailField(max_length=500,blank=True,null=True)
+    username = models.CharField(max_length=200,blank=True,null=True)
+    location = models.CharField(max_length=200,blank=True,null=True)
+    short_intro = models.CharField(max_length=200,blank=True,null=True)
+    bio = models.TextField(blank=True,null=True)
+    profile_image = models.ImageField(null=True,blank=True,upload_to='profiles/', default="prfiles/user-default.png")
+    social_github = models.CharField(max_length=200,blank=True,null=True)
+    social_twitter = models.CharField(max_length=200,blank=True,null=True)
+    social_linkedin = models.CharField(max_length=200,blank=True,null=True)
+    social_website = models.CharField(max_length=200,blank=True,null=True)
+    created = models.DateTimeField(auto_now_add=True)
+    id = models.UUIDField(default=uuid.uuid4,unique=True,primary_key=True,editable=False)
+
+    def __str__(self):
+        return str(self.user.username)
+    
+class Skill(models.Model):
+    owner = models.ForeignKey(Profile, on_delete=models.CASCADE, null=True, blank=True)
+    name = models.CharField(max_length=200,blank=True,null=True)
+    description = models.TextField(null=True,blank=True)
+    created = models.DateTimeField(auto_now_add=True)
+    id = models.UUIDField(default=uuid.uuid4, unique = True,primary_key=True,editable=False)
+
+    def __str__(self):
+        return str(self.name)

### 2023-03-06 django/formEditorJS/form.js

@@ -1,0 +1,313 @@
+// const e = require("cors");
+
+var inputContainers = 0;
+var inputLabels = 0;
+var inputs = 0;
+var hue = 0;
+var newColor;
+
+function addElement() {
+    newColor = generateRandomHSV(hue);
+
+    // create a new div element
+    var newDivID = "inputContainer" + inputContainers;
+    var newDiv = document.createElement("div");
+    newDiv.setAttribute("class", "inputContainer");
+    newDiv.setAttribute("id", newDivID); // set id here
+    console.log(newDivID);
+    // document.getElementById(newDivID).getParent().removeChild(newDivID);
+
+    // create a new button element - for delete button
+    var newDeleteButton = document.createElement("button");
+    newDeleteButton.setAttribute("type", "button");
+    newDeleteButton.setAttribute("id", "button" + inputContainers); // set id here
+    newDeleteButton.setAttribute("onclick", "deleteElement(" + newDivID + ")");
+    newDeleteButton.setAttribute("class", "deleteButton");
+    newDeleteButton.innerHTML = "X";
+
+
+    // create a new input element - for input name
+    var newInput = document.createElement("input");
+    newInput.setAttribute("type", "text");
+    newInput.setAttribute("id", "input" + inputs); // set id here
+    // newInput.setAttribute("value", "input_" + inputs)
+    newInput.setAttribute("placeholder", "Enter your inqury here...");
+    newInput.setAttribute("class", "formElements");
+
+
+    // create a new select element - for input type
+    var selectID = "select" + inputs;
+    var newSelect = document.createElement("select");
+    newSelect.setAttribute("id", selectID); // set id here
+    newSelect.setAttribute("class", "formElements");
+    newSelect.setAttribute("onchange", "checkSelect("+ selectID +")");
+
+
+    // create a new option element - for input type
+    var options = ['text-field', 'true-false', 'attitude-scale'];
+    for (var i = 0; i < options.length; i++) {
+        var opt = options[i];
+        var el = document.createElement("option");
+        el.textContent = opt;
+        el.value = opt;
+        newSelect.appendChild(el);
+    }
+
+
+    // add the newly created element and its content into the DOM
+    document.getElementById("form-elements").appendChild(newDiv);
+    document.getElementById("inputContainer" + inputContainers).appendChild(newDeleteButton);
+    document.getElementById("inputContainer" + inputContainers).appendChild(newSelect);
+    document.getElementById("inputContainer" + inputContainers).appendChild(newInput);
[…]

### 2023-03-06 paper/main.tex
updated paper

@@
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf} 
+\documentclass[letterpaper, 12 pt, conference]{ieeeconf} 
 \IEEEoverridecommandlockouts                              
 \overrideIEEEmargins
+\usepackage{setspace}
 
@@
 %\usepackage{mathptmx} % assumes new font selection scheme installed
-%\usepackage{times} % assumes new font selection scheme installed
+\usepackage{times} % assumes new font selection scheme installed
 %\usepackage{amsmath} % assumes amsmath package installed
@@
 \input{titlepage}
-%%%%%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-\end{abstract}
 
@@
 
+\doublespacing 
+\onecolumn
+
 \section{Problem Definition}
-\subsection{outline the problem requirements and include the ap- plication domain and motivations of your project (1 page).}
-Develop a software that facilitates administration of surveys and feedback collection. The software must be fast, robust, and friendly.
+\subsection{outline the problem requirements and include the application domain and motivations of your project (1 page).}
 
-Marketing/Business Operations
+Business and product owners want meaningful feedback from their customers to assist in their growth and success.
+It can be difficult to collect this information without onsite hardware and processing the data provided can be a timely task.
+As with many forms of customer engagement and ratings, customers can be unwilling to participate in traditional methods of feedback if too many steps are required, so the data collected will not be an accurate portrayal of opinions.
 
-Businesses want meaningful direct feedback on their products and services.
-Our project aims to provide a generalized solution to context-specific customer feedback monitoring without the need of onsite hardware to capture responses.
-In other terms, our app is a solution for conducting self-administered surveys.
+In order to solve this problem, we have created a web application that allows for customers to provide their feedback in a simplistic way, and displays this information for businesses or owners in a way that it simple to understand without the need for onsite hardware.
+By allowing the customer to interact with a site that is not cumbersome, and can be done from the convenience of their smart phone, many more customers will be willing to submit their thoughts and opinions.
+
+\newpage    
+\section{Application Benefits}
+\subsection{what are the benefits of your application when compared to existing systems. Choose two systems only and include their references (2 pages).}
 
@@
 
-\section{Application Benefits}
-\subsection{what are the benefits of your application when compared to existing systems. Choose two systems only and include their references (2 pages).}
+\textbf{discuss survey monkey differences}
 
+\textbf{discuss questionpro differences}
+
+\newpage
 \section{Requirements Elicitation and Specification}
-\subsection{Functional requirements list (only the ones that you have imple- mented) for each user role (two exactly). Name each requirement and explain it briefly.}
+\subsection{Functional requirements list (only the ones that you have implemented) for each user role (two exactly). Name each requirement and explain it briefly.}
 \subsection{For each user role, provide the use case diagram with all the use cases and actors.}
@@
 For each class, provide the data types of the attributes and prototypes of the methods.}
-\subsection{Provide the class diagram of the whole system by incorporating the two design patterns.
-}
+\subsection{Provide the class diagram of the whole system by incorporating the two design patterns.}
 
@@
 
-\section{Conclusion}
-
 \addtolength{\textheight}{-12cm}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Appendix}
 
-Appendixes should appear before the acknowledgment.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.
+\newpage
 

### 2023-03-06 paper/main.tex
added links and images to paper

@@
 \usepackage{setspace}
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    urlcolor=blue,
+    }
+
+\urlstyle{same}
+\usepackage{wrapfig}
 
@@
 \subsection{Functional requirements list (only the ones that you have implemented) for each user role (two exactly). Name each requirement and explain it briefly.}
-\subsection{For each user role, provide the use case diagram with all the use cases and actors.}
-\subsection{Describe in detail two use cases using the activity diagram. Choose the most complex use cases.}
-\subsection{Software qualities: Correctness, Time-eﬀiciency and Robustness.
-In- clude at least two concrete examples for each quality for each user role.
-The sign-in and sign-up use cases are excluded from the examples.
-}
-
-Two types of users/roles: Feedback Gatherer / Respondent.
 
 \textbf{Feedback Gatherer}
-
-    Register: Feedback gatherer creates an account by entering the required information
-
-    Create Survey: Feedback gatherer creates a survey by entering questions and selecting type of responses
-
-    View QR Code: Feedback gatherer views the generated QR code for the survey
-
-    Delete Survey: Feedback gatherer deletes a survey that is no longer required
-
-    View Statistics and responses: Feedback gatherer views statistics and responses of a selected survey
+\begin{enumerate}
+   \item \textbf{Register:} Feedback gatherer creates an account by entering the required information
+   \item \textbf{Create Survey:} Feedback gatherer creates a survey by entering questions and selecting type of responses
+   \item \textbf{View QR Code:} Feedback gatherer views the generated QR code for the survey
+   \item \textbf{Delete Survey:} Feedback gatherer deletes a survey that is no longer required
+   \item \textbf{View Statistics and Responses:} Feedback gatherer views statistics and responses of a selected survey
+\end{enumerate}
 
 \textbf{Respondent}
+\begin{enumerate}
+   \item \textbf{Scan QR Code:} Respondent scans the QR code to view the survey
+   \item \textbf{Enter Responses:} Respondent enters responses to the survey questions
+   \item \textbf{Submit Response:} Respondent submits responses to the survey questions
+\end{enumerate}
 
-    Scan QR Code: Respondent scans the QR code to view the survey
+%\newpage
 
-    Enter responses: Respondent enters responses to the survey questions
+\subsection{For each user role, provide the use case diagram with all the use cases and actors.}
+\includegraphics[width=0.70\textwidth]{caseDiagram.png}
 
-    Submit: Respondent submits responses to the survey questions
-
-The feedback gatherer can create a survey after registering.
+\newpage
+\subsection{Describe in detail two use cases using the activity diagram. Choose the most complex use cases.}
+\begin{enumerate}
+    \item The feedback gatherer can create a survey after registering.
 The feedback gatherer has the option to delete an existing survey or view statistics and responses to an existing survey.
 After creating a survey, the feedback gatherer can view the QR code to administer the created survey.
+    \includegraphics[width=0.70\textwidth]{feedbackGatherer.png}
+\newpage
+    \item The respondent can scan the QR code to take a survey created by a feedback gatherer. The respondent enters responses to the survey and submit the responses.
+    \includegraphics[width=0.70\textwidth]{respondent.png}
+\end{enumerate}
 
-The respondent can scan the QR code to take a survey created by a feedback gatherer. The respondent enters responses to the survey and submit the responses.
+\subsection{Software qualities: Correctness, Time-eﬀiciency and Robustness.
+Include at least two concrete examples for each quality for each user role.
+The sign-in and sign-up use cases are excluded from the examples.}
+
+\textbf{Correctness:}
+\begin{enumerate}
+    \item[] Feedback Gatherer:
+    \begin{itemize}
+        \item A survey correctly displays the questions and answer choices entered by the feedback gatherer during creation. 
+        \item Accurate statistics for a survey are shown to the feedback gatherer.
+    \end{itemize}
+    \item[] Respondent:
+    \begin{itemize}
+        \item Scanning the QR code takes the respondent to the correct survey.
+        \item Responses to a survey are saved correctly.
+    \end{itemize}
+\end{enumerate}
+
+\textbf{Time Efficiency:}
+\begin{enumerate}
+    \item[] Feedback Gatherer:
+    \begin{itemize}
+        \item  When a feedback gatherer creates the survey, the QR code for the survey is created in a timely manner.
+        \item When responses to a survey are submitted, they are available for view by the feedback gatherer in a timely manner.
+    \end{itemize}
+    \item[] Respondent:
+    \begin{itemize}
+        \item A respondent is taken to the survey in a timely manner after scanning a QR code for a survey.
+        \item A respondent is given a confirmation in a timely manner after submitting a survey.
+    \end{itemize}
+\end{enumerate}
+
+\textbf{Robustness:}
+\begin{enumerate}
+    \item[] Feedback Gatherer:
+    \begin{itemize}
+        \item  If a feedback gatherer attempts to submit a blank survey, submission is denied with a warning.
+        \item If a feedback gatherer forgets to select a type of answer to a question, submission is denied with a warning.
+    \end{itemize}
+    \item[] Respondent:
+    \begin{itemize}
+        \item If a respondent attempts to submit a survey with one or more unanswered questions, submission is denied and unanswered questions are marked.
+        \item If a respondent attempts to exit the survey after answering one or more questions, a warning is shown.
+    \end{itemize}
+\end{enumerate}
 
@@
 Website builders, such as Wordpress, are not allowed.}
-\subsection{Link of your Web-based application. The application should be acces- sible online and runnable.}
+\url{https://github.com/zachary-huber/feedback-app}
+
+\subsection{Link of your Web-based application. The application should be accessible online and runnable.}
+\url{https://www.viewnote.app/}
 
@@
 \subsection{List of programming languages.}
+\begin{enumerate}
+   \item Javascript
+   \item HTML
+   \item CSS
+   \item PHP
+\end{enumerate}
+
 \subsection{List of reused algorithms and programs. Include their sources.}
+\begin{enumerate}
+   \item thing
+   \begin{description}
+     \item description
+   \end{description}
+   \item thing
+\end{enumerate}
+
 \subsection{List of software tools and environments. Provide briefly their benefits specifically for your application.}
+\begin{enumerate}
+   \item React
+   \begin{description}
+     \item description
+   \end{description}
+   \item Django
+\end{enumerate}
 

### 2023-03-14 django/dLocal/dLocal/projects/migrations/0005_alter_form_created.py
updated models

@@ -1,0 +1,18 @@
+# Generated by Django 4.1.7 on 2023-03-13 18:58
+
+from django.db import migrations, models
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ("projects", "0004_project_owner"),
+    ]
+
+    operations = [
+        migrations.AlterField(
+            model_name="form",
+            name="created",
+            field=models.DateTimeField(),
+        ),
+    ]

### 2023-03-14 django/dLocal/dLocal/projects/migrations/0006_forms_projectsform.py

@@ -1,0 +1,49 @@
+# Generated by Django 4.1.7 on 2023-03-13 19:32
+
+from django.db import migrations, models
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ("projects", "0005_alter_form_created"),
+    ]
+
+    operations = [
+        migrations.CreateModel(
+            name="Forms",
+            fields=[
+                ("form_id", models.AutoField(primary_key=True, serialize=False)),
+                ("user_id", models.IntegerField(blank=True, null=True)),
+                ("title", models.CharField(blank=True, max_length=255, null=True)),
+                (
+                    "description",
+                    models.CharField(blank=True, max_length=255, null=True),
+                ),
+                ("created_at", models.DateTimeField(blank=True, null=True)),
+                ("updated_at", models.DateTimeField(blank=True, null=True)),
+                ("is_active", models.IntegerField(blank=True, null=True)),
+                (
+                    "form_json",
+                    models.TextField(blank=True, db_column="form_JSON", null=True),
+                ),
+            ],
+            options={
+                "db_table": "forms",
+                "managed": False,
+            },
+        ),
+        migrations.CreateModel(
+            name="ProjectsForm",
+            fields=[
+                ("id", models.AutoField(primary_key=True, serialize=False)),
+                ("created_at", models.DateTimeField(blank=True, null=True)),
+                ("title", models.CharField(blank=True, max_length=200, null=True)),
+                ("description", models.TextField(blank=True, null=True)),
+            ],
+            options={
+                "db_table": "projects_form",
+                "managed": False,
+            },
+        ),
+    ]

### 2023-03-14 django/dLocal/dLocal/projects/models.py

@@ -64,3 +64,29 @@ class Response(models.Model):
     response_text = models.TextField(null=True,blank=True)
     def __str__(self):
         return self.id
+
+
+class ProjectsForm(models.Model):
+    id = models.AutoField(primary_key=True)
+    created_at = models.DateTimeField(blank=True, null=True)
+    title = models.CharField(max_length=200, blank=True, null=True)
+    description = models.TextField(blank=True, null=True)
+
+    class Meta:
+        managed = False
+        db_table = 'projects_form'
+        
+        
+class Forms(models.Model):
+    form_id = models.AutoField(primary_key=True)
+    user_id = models.IntegerField(blank=True, null=True) #models.ForeignKey('Users', models.DO_NOTHING, blank=True, null=True)
+    title = models.CharField(max_length=255, blank=True, null=True)
+    description = models.CharField(max_length=255, blank=True, null=True)
+    created_at = models.DateTimeField(blank=True, null=True)
+    updated_at = models.DateTimeField(blank=True, null=True)
+    is_active = models.IntegerField(blank=True, null=True)
+    form_json = models.TextField(db_column='form_JSON', blank=True, null=True)  # Field name made lowercase.
+
+    class Meta:
+        managed = False
+        db_table = 'forms'

### 2023-03-14 django/dLocal/dLocal/projects/views.py

@@ -7,7 +7,7 @@ from django.contrib.auth.decorators import login_required
 
 import json
 from django.http import JsonResponse
-from .models import Form
+from .models import Forms
 from django.contrib import messages
 
 # Create your views here.
@@ -73,7 +73,10 @@ def saveFormEditor(request):
             json_data = request.body.decode('utf-8')  # decode the request body
             user_id = request.user.id
             
-            form = Form(id=1, description=json_data, title="newForm")  # create a Form object with the JSON data
+            # get the form title from the JSON data
+            newFormTitle = list(json.loads(json_data)[0].values())[0]
+            
+            form = Forms(form_json=json_data, user_id=user_id, title=newFormTitle)  # create a Form object with the JSON data
             form.save()  # save the Form object to the database
             return JsonResponse({'status': 'ok'})
         else:

### 2023-03-14 django/dLocal/dLocal/static/js/form.js

@@ -324,7 +324,7 @@ function getCookie(name) {
 const csrftoken = getCookie('csrftoken');
 
 function sendData() {
-    var myVariable = "saveForm()";
+    var myVariable = saveForm();
     fetch('/../saveFormEditor/', {
     method: 'POST',
     headers: {

### 2023-03-14 django/dLocal/dLocal/users/models.py

@@ -32,3 +32,18 @@ class Skill(models.Model):
 
     def __str__(self):
         return str(self.name)
+    
+    
+class Forms(models.Model):
+    form_id = models.AutoField(primary_key=True)
+    user_id = models.IntegerField(blank=True, null=True) #models.ForeignKey('Users', models.DO_NOTHING, blank=True, null=True)
+    title = models.CharField(max_length=255, blank=True, null=True)
+    description = models.CharField(max_length=255, blank=True, null=True)
+    created_at = models.DateTimeField(blank=True, null=True)
+    updated_at = models.DateTimeField(blank=True, null=True)
+    is_active = models.IntegerField(blank=True, null=True)
+    form_json = models.TextField(db_column='form_JSON', blank=True, null=True)  # Field name made lowercase.
+
+    class Meta:
+        managed = False
+        db_table = 'forms'

### 2023-03-14 django/dLocal/dLocal/users/views.py

@@ -7,6 +7,8 @@ from django.contrib.auth.decorators import login_required
 from django.contrib import messages
 from .forms import CustomUserCreationForm
 
+from .models import Forms
+
 # Create your views here.
 
 def loginUser(request):
@@ -66,6 +68,9 @@ def registerUser(request):
 def profiles(request):
     profiles = Profile.objects.all()
     context = {'profiles':profiles}
+    
+    Forms = Forms.objects.get(user_id=user_id)
+    
     return render(request, 'users/profiles.html', context)
 
 def userProfile(request, pk):

### 2023-03-14 django/dLocal/dLocal/users/views.py
fixed 'Forms' bug

@@ -69,7 +69,7 @@ def profiles(request):
     profiles = Profile.objects.all()
     context = {'profiles':profiles}
     
-    Forms = Forms.objects.get(user_id=user_id)
+    # Forms = Forms.objects.get(user_id=user_id)
     
     return render(request, 'users/profiles.html', context)
 

### 2023-03-14 paper/main.tex
updates to paper

@@
 \section{Problem Definition}
-\subsection{outline the problem requirements and include the application domain and motivations of your project (1 page).}
-
+\subsection{Outline the problem requirements and include the application domain and motivations of your project (1 page).}
+\linebreak
 Business and product owners want meaningful feedback from their customers to assist in their growth and success.
@@
 As with many forms of customer engagement and ratings, customers can be unwilling to participate in traditional methods of feedback if too many steps are required, so the data collected will not be an accurate portrayal of opinions.
+\newline
 
@@
 By allowing the customer to interact with a site that is not cumbersome, and can be done from the convenience of their smart phone, many more customers will be willing to submit their thoughts and opinions.
+\newline
+
+Our web application is created specifically to benefit business owners or managers who want to monitor the opinions of their clientele in a simplistic way.
+Based on our previous experiences, these surveys for clientele are often annoying to complete or difficult to find.
+Often they require typing in a website manually from the back of a receipt which is not worth most people's time.
+By creating a website that consolidates everything to a simple QR code that can be scanned by a smart phone either posted at the physical location to be rated, or printed on a receipt to be done after the fact.
+\newline
+
+By making surveys more accessible and simple to fill out, more people will be willing to participate, making survey results more accurate.
+As of now, most people who leave reviews or fill out surveys have extreme opinions which may sway the results in one way or another, so by creating this application, we have hopes that more people will share their opinions making the results much more well rounded.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \section{Application Benefits}
-\subsection{what are the benefits of your application when compared to existing systems. Choose two systems only and include their references (2 pages).}
-
+\subsection{What are the benefits of your application when compared to existing systems. Choose two systems only and include their references (2 pages).}
+\linebreak
 Our application is a simple tool for conducting self-administered surveys.
@@
 QR codes can be generated for wide distribution and quick access.
-SurveyMonkey (https://www.surveymonkey.com/) and QuestionPro (https://www.questionpro.com/) are comparable existing systems.
+SurveyMonkey (\url{https://www.surveymonkey.com/}) and QuestionPro (\url{https://www.questionpro.com/}) are comparable existing systems.
 Some benefits of our application are that the users can received unlimited number of responses for their surveys without cost and all features to create the surveys are free as well.
@@
 Respondents do not need to create an account to respond to surveys.
+\hfill \break
 
-\textbf{discuss survey monkey differences}
+\subsubsection*{Survey Monkey}
 
-\textbf{discuss questionpro differences}
+Survey Monkey is one of the more popular survey platforms as of now.
+It has lots of different options for different groups of people who may be interested in gaining an insight into people's opinions.
+With its wide array of available options, it is what many people think of when someone mentions a survey website.
+\newline
+
+Survey Monkey's website is very overwhelming to look at on first glance, but after a bit of digging you are able to find a bit of information on the packages available.
+In the past, they have had a pretty large amount of features for free users, but now their free package is very limited.
+Currently, their free package only allows for unlimited surveys, but with a restriction of 10 questions each, and only allows for a limited amount of responses.
+This means that if you want to get information with a large group of people, you would have to create multiples of the same surveys and compile the data together manually.
+
+\hfill \break
+\subsubsection*{QuestionPro}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \subsection{Functional requirements list (only the ones that you have implemented) for each user role (two exactly). Name each requirement and explain it briefly.}
+\linebreak
 
@@
 \end{enumerate}
+\newline 
+\hfill \break
 
@@
 
-%\newpage
+\newpage
 
 \subsection{For each user role, provide the use case diagram with all the use cases and actors.}
+\hfill \break
+
 \includegraphics[width=0.70\textwidth]{caseDiagram.png}
@@
 After creating a survey, the feedback gatherer can view the QR code to administer the created survey.
+    \hfill \break
+
     \includegraphics[width=0.70\textwidth]{feedbackGatherer.png}
@@
     \item The respondent can scan the QR code to take a survey created by a feedback gatherer. The respondent enters responses to the survey and submit the responses.
+    \linebreak
+    \hfill \break
     \includegraphics[width=0.70\textwidth]{respondent.png}
+
 \end{enumerate}
+\hfill \break
 
@@
 The sign-in and sign-up use cases are excluded from the examples.}
-
+\linebreak
+    \hfill \break
 \textbf{Correctness:}
@@
 \end{enumerate}
+\hfill \break
 
@@
 
+\hfill \break
+
 \textbf{Robustness:}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Top-level and Low-level Software Design}
 \subsection{Provide the MVC architecture according to the selected Web frame- work. Also, describe at least three benefits of MVC for your application.}
+\linebreak
+    \hfill \break
+
 \subsection{Observer and Factory design patterns.
@@
 For each class, provide the data types of the attributes and prototypes of the methods.}
+\linebreak
+    \hfill \break
+
 \subsection{Provide the class diagram of the whole system by incorporating the two design patterns.}
+\linebreak
+    \hfill \break
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \subsection{Submit the screenshot of the entire structure of the code within the web framework.}
+\linebreak
+    \hfill \break
+
 \subsection{Deployment diagram regarding the hardware configuration of the code. Indicate the supported Web browsers, the application/Web servers and the database solution.}
+\linebreak
+    \hfill \break
+
 \subsection{Screenshots of all table contents of the system data.}
+\linebreak
+    \hfill \break
+
 \subsection{GitHub link of the entire program.
@@
 Website builders, such as Wordpress, are not allowed.}
+\linebreak
+    \hfill \break
 \url{https://github.com/zachary-huber/feedback-app}
+\hfill \break
 
 \subsection{Link of your Web-based application. The application should be accessible online and runnable.}
+\linebreak
+    \hfill \break
 \url{https://www.viewnote.app/}
+\hfill \break
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Acceptance Testing: select test cases for both user roles. The sign-in and sign-up are excluded from testing.}
-\subsection{Correctness testing using four test cases (screenshots of both inputs and out- puts).}
-\subsection{Robustness testing using four test cases (screenshots of both inputs and out- puts).}
+\subsection{Correctness testing using four test cases (screenshots of both inputs and outputs).}
+\subsection{Robustness testing using four test cases (screenshots of both inputs and outputs).}
 \subsection{Time-eﬀiciency testing of two functions (with screenshots). Indicate the method you used to measure the time.}
@@
 
-\begin{thebibliography}{99}
+%\begin{thebibliography}{99}
 
-\bibitem{young-1964} G.
+%\bibitem{young-1964} G.
 O.
@@
 15Ð64.
-\bibitem{chen-1993} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
-\bibitem{poor-1985} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
+%\bibitem{chen-1993} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
+%\bibitem{poor-1985} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
 
-\bibitem{uofr} "Home", University of Regina, 2022. [Online]. Available: https://www.uregina.ca/. [Accessed: 06- Apr- 2022].
+%\bibitem{uofr} "Home", University of Regina, 2022. [Online]. Available: https://www.uregina.ca/. [Accessed: 06- Apr- 2022].
 
-\end{thebibliography}
+%\end{thebibliography}
 

### 2023-03-14 django/dLocal/dLocal/CS476P/settings.py
added users forms list to profiles.html

@@ -102,6 +102,8 @@ DATABASES = {
 }
 
 
+
+
 # Password validation
 # https://docs.djangoproject.com/en/4.1/ref/settings/#auth-password-validators
 

### 2023-03-14 django/dLocal/dLocal/projects/models.py

@@ -2,7 +2,7 @@ from django.db import models
 from django.contrib.auth.models import User
 import uuid
 from users.models import Profile
-
+from users.models import User
 # Create your models here.
 
 class Project(models.Model):
@@ -79,7 +79,8 @@ class ProjectsForm(models.Model):
         
 class Forms(models.Model):
     form_id = models.AutoField(primary_key=True)
-    user_id = models.IntegerField(blank=True, null=True) #models.ForeignKey('Users', models.DO_NOTHING, blank=True, null=True)
+    user_id = models.IntegerField(blank=True, null=True) 
+    # user_id = models.ForeignKey('User', models.DO_NOTHING, blank=True, null=True)
     title = models.CharField(max_length=255, blank=True, null=True)
     description = models.CharField(max_length=255, blank=True, null=True)
     created_at = models.DateTimeField(blank=True, null=True)

### 2023-03-14 django/dLocal/dLocal/projects/urls.py

@@ -10,6 +10,7 @@ urlpatterns = [
     path('QRcode/', views.QRcode, name="QRcode"),
     path('signup/', views.signup, name="signup"),
     path('survey/', views.survey, name="survey"),
+    path('survey/<int:form_id>', views.survey, name="survey"),
     path('thanks/', views.thanks, name="thanks"),
     path('formEditor/', views.formEditor, name="formEditor"),
     path('saveFormEditor/', views.saveFormEditor, name="saveFormEditor"),

### 2023-03-14 django/dLocal/dLocal/projects/views.py

@@ -10,6 +10,8 @@ from django.http import JsonResponse
 from .models import Forms
 from django.contrib import messages
 
+from users.models import User
+
 # Create your views here.
 
 def home(request):

### 2023-03-14 django/dLocal/dLocal/users/views.py

@@ -7,7 +7,7 @@ from django.contrib.auth.decorators import login_required
 from django.contrib import messages
 from .forms import CustomUserCreationForm
 
-from .models import Forms
+from projects.models import Forms
 
 # Create your views here.
 
@@ -65,11 +65,32 @@ def registerUser(request):
     return render(request, 'users/login_register.html', context)
 
 
+def user_forms(request, idd):
+    # Retrieve the user object based on the user_id
+    user_id = User.objects.get(id=idd)
+
+    # Retrieve all forms associated with the user
+    user_forms = Forms.objects.filter(user_id=idd)
+
+    form_ids = []
+    form_titles = []
+    for user_form in user_forms:
+        form_ids.append(user_form.form_id)
+        form_titles.append(user_form.title)
+        
+    forms = zip(form_ids, form_titles)
+    print(forms)
+    # get form title from user_forms
+    
+    # passing the user_id, user_forms, form_ids, and form_titles to the profiles.html template
+    return render(request, 'users/profiles.html',  {'id': user_id, 'forms': forms})
+
+
 def profiles(request):
     profiles = Profile.objects.all()
     context = {'profiles':profiles}
-    
-    # Forms = Forms.objects.get(user_id=user_id)
+    user_id = request.user.id
+    return user_forms(request, user_id)
     
     return render(request, 'users/profiles.html', context)
 

### 2023-03-15 paper/main.tex
first two sections completed for paper

@@
 Respondents do not need to create an account to respond to surveys.
-\hfill \break
 
-\subsubsection*{Survey Monkey}
+\hfill
+
+\subsubsection*{Survey Monkey}\hfill
 
@@
 This means that if you want to get information with a large group of people, you would have to create multiples of the same surveys and compile the data together manually.
+\newline
 
-\hfill \break
-\subsubsection*{QuestionPro}
+Overall, SurveyMonkey is a good tool for users who want to create surveys quickly and easily, but it may not be the best fit for people who want more expansive options for length of survey, and ability to view feedback.
+The limited free plan and cost may also be a reason for people to choose an alternative.
+
+\break
+\subsubsection*{QuestionPro}\hfill
+
+QuestionPro, similar to Survey Monkey, has many different options depending on the customer and type of data they want to collect.
+It has many of the same options as Survey Monkey has when it comes to questions type, but seems like it's list of features might be more expansive.
+\newline
+
+QuestionPro has a very similar home page to Survey Monkey, but made it easier to find the differences between their packages available.
+This site has many more features available for free users than Survey Monkey, but still has a limit to the amount of questions and responses unless you pay.
+Rather than limiting to 10 question per survey, QuestionPro allows free users to have up to 100 questions per survey with up to 300 responses which is a very large increase in comparison to Survey Monkey.
+\newline
+
+QuestionPro is definitely a powerful tool for creating surveys online, but may be confusing for users with limited technology experiences.
+The cost for full access is also a restriction for some, but in comparison to Survey Monkey, the free version includes a much larger amount of features and usability.
+\newline
+
+Both of these other platforms for similar survey creation to ours lock many features behind a paywall.
+Our goal to create a very simple survey platform eliminates the confusion from having too many options or limited response allowances to make it more user friendly.
+We also only have a free option available for all users, so no features are hidden behind a paywall, allowing everyone to have the same experience while using it.
 
@@
 \begin{enumerate}
-   \item \textbf{Register:} Feedback gatherer creates an account by entering the required information
-   \item \textbf{Create Survey:} Feedback gatherer creates a survey by entering questions and selecting type of responses
-   \item \textbf{View QR Code:} Feedback gatherer views the generated QR code for the survey
-   \item \textbf{Delete Survey:} Feedback gatherer deletes a survey that is no longer required
-   \item \textbf{View Statistics and Responses:} Feedback gatherer views statistics and responses of a selected survey
+   \item \textbf{Register:} Feedback gatherer creates an account by entering the required information. 
+   \item \textbf{Create Survey:} Feedback gatherer creates a survey by entering questions and selecting type of responses.
+   \item \textbf{View QR Code:} Feedback gatherer views the generated QR code for the survey.
+   \item \textbf{Delete Survey:} Feedback gatherer deletes a survey that is no longer required.
+   \item \textbf{View Statistics and Responses:} Feedback gatherer views statistics and responses of a selected survey.
 \end{enumerate}
+
 \newline 
@@
 \begin{enumerate}
-   \item \textbf{Scan QR Code:} Respondent scans the QR code to view the survey
-   \item \textbf{Enter Responses:} Respondent enters responses to the survey questions
-   \item \textbf{Submit Response:} Respondent submits responses to the survey questions
+   \item \textbf{Scan QR Code:} Respondent scans the QR code to view the survey.
+   \item \textbf{Enter Responses:} Respondent enters responses to the survey questions.
+   \item \textbf{Submit Response:} Respondent submits responses to the survey questions.
 \end{enumerate}

### 2023-03-15 django/dLocal/dLocal/projects/views.py
added survey viewer code

@@ -11,6 +11,7 @@ from .models import Forms
 from django.contrib import messages
 
 from users.models import User
+from projects.models import Forms
 
 # Create your views here.
 
@@ -42,6 +43,15 @@ def signup(request):
 
 def survey(request):
     return render(request, 'projects/Survey.html')
+
+def survey(request, form_id):
+    # form = Forms.objects.get(id=form_id)
+    # form_JSON = form.form_json
+    # form_titles = form.title
+    
+    # Do any additional processing or rendering here
+    # return render(request, 'survey.html', {'form': form})
+    return render(request, 'projects/Survey.html', {'form_id': form_id})
 
 def thanks(request):
     return render(request, 'projects/Thanks.html')

### 2023-03-15 django/dLocal/dLocal/static/js/survey.js

@@ -1,0 +1,358 @@
+// const e = require("cors");
+
+var inputContainers = 0;
+var inputLabels = 0;
+var inputs = 0;
+var hue = 0;
+var newColor;
+
+function addElement() {
+    newColor = generateRandomHSV(hue);
+
+    // create a new div element
+    var newDivID = "inputContainer" + inputContainers;
+    var newDiv = document.createElement("div");
+    newDiv.setAttribute("class", "inputContainer");
+    newDiv.setAttribute("id", newDivID); // set id here
+    console.log(newDivID);
+    // document.getElementById(newDivID).getParent().removeChild(newDivID);
+
+    // create a new button element - for delete button
+    var newDeleteButton = document.createElement("button");
+    newDeleteButton.setAttribute("type", "button");
+    newDeleteButton.setAttribute("id", "button" + inputContainers); // set id here
+    newDeleteButton.setAttribute("onclick", "deleteElement(" + newDivID + ")");
+    newDeleteButton.setAttribute("class", "deleteButton");
+    newDeleteButton.innerHTML = "X";
+
+
+    // create a new input element - for input name
+    var newInput = document.createElement("input");
+    newInput.setAttribute("type", "text");
+    newInput.setAttribute("id", "input" + inputs); // set id here
+    // newInput.setAttribute("value", "input_" + inputs)
+    newInput.setAttribute("placeholder", "Enter your inqury here...");
+    newInput.setAttribute("class", "formElements");
+
+
+    // create a new select element - for input type
+    var selectID = "select" + inputs;
+    var newSelect = document.createElement("select");
+    newSelect.setAttribute("id", selectID); // set id here
+    newSelect.setAttribute("class", "formElements");
+    newSelect.setAttribute("onchange", "checkSelect("+ selectID +")");
+
+
+    // create a new option element - for input type
+    var options = ['text-field', 'true-false', 'attitude-scale'];
+    for (var i = 0; i < options.length; i++) {
+        var opt = options[i];
+        var el = document.createElement("option");
+        el.textContent = opt;
+        el.value = opt;
+        newSelect.appendChild(el);
+    }
+
+
+    // add the newly created element and its content into the DOM
+    document.getElementById("form-elements").appendChild(newDiv);
+    document.getElementById("inputContainer" + inputContainers).appendChild(newDeleteButton);
+    document.getElementById("inputContainer" + inputContainers).appendChild(newSelect);
+    document.getElementById("inputContainer" + inputContainers).appendChild(newInput);
+    
[…]

### 2023-03-15 django/CS476P/CS476P/users/views.py
Update views.py

@@ -7,6 +7,13 @@ from django.contrib.auth.decorators import login_required
 from django.contrib import messages
 from .forms import CustomUserCreationForm
 
+import json
+from django.http import JsonResponse
+from .models import Forms
+from django.contrib import messages
+
+
+
 # Create your views here.
 
 def loginUser(request):
@@ -79,3 +86,42 @@ def userAccount(request):
     context = {'profile':profile}
     return render(request, 'users/account.html', context)
 
+
+@login_required
+def formEditor(request):
+    return render(request, 'users/formEditor.html')
+    # if request.method == 'POST':
+        
+    #     my_variable = request.POST.get('myVariable', None)
+    #     user_id = request.user.id
+    #     try:
+    #         json_data = json.loads(my_variable)
+    #     except ValueError:
+    #         return JsonResponse({'status': 'error', 'message': 'Invalid JSON data'})
+    #     form = Form(user_id=user_id, json_data=json_data)
+    #     form.save()
+    #     return JsonResponse({'status': 'ok'})
+    #     return HttpResponse('Form submitted')
+    # else:
+    #     render(request, 'projects/formEditor.html')
+    #     return HttpResponse('Form submitted')
+    
+    
+@login_required
+def saveFormEditor(request):   
+    # return render(request, 'projects/saveFormEditor.html')
+    if request.user.is_authenticated:
+        if request.method == 'POST':
+            json_data = request.body.decode('utf-8')  # decode the request body
+            user_id = request.user.id
+            
+            # get the form title from the JSON data
+            newFormTitle = list(json.loads(json_data)[0].values())[0]
+            
+            form = Forms(form_json=json_data, user_id=user_id, title=newFormTitle)  # create a Form object with the JSON data
+            form.save()  # save the Form object to the database
+            return JsonResponse({'status': 'ok'})
+        else:
+            return JsonResponse({'status': 'error', 'message': 'Invalid request method'})
+    else:
+        return JsonResponse({'status': 'error', 'message': 'User is not authenticated'})

### 2023-03-15 django/CS476P/CS476P/users/urls.py
Update urls.py

@@ -10,4 +10,9 @@ urlpatterns = [
     path('profiles/<str:pk>/', views.userProfile, name="user-profile"),
 
     path('account/', views.userAccount, name="account"),   
+    path('test/', views.tests, name="test123"),
+    #path('createsurvey/', views.saveFormEditor, name='form'),
+    path('formEditor/', views.formEditor, name="formEditor"),
+    #path('createsurvey/', views.saveFormEditor, name="saveFormEditor"),
+    path('saveformeditor/', views.saveFormEditor, name="saveFormEditor"),
 ]

### 2023-03-15 django/CS476P/CS476P/users/models.py
Update models.py

@@ -32,3 +32,35 @@ class Skill(models.Model):
 
     def __str__(self):
         return str(self.name)
+    
+    
+    
+    
+    
+    class Test(models.Model):
+    name = models.CharField(max_length=200,blank=True,null=True)
+    description = models.TextField(null=True,blank=True)
+    created = models.DateTimeField(auto_now_add=True)
+    id = models.UUIDField(default=uuid.uuid4, unique = True,primary_key=True,editable=False)
+    def __str__(self):
+        return str(self.name)
+    
+
+
+
+
+
+
+
+class Forms(models.Model):
+    form_id = models.AutoField(primary_key=True)
+    user_id = models.IntegerField(blank=True, null=True) #models.ForeignKey('Users', models.DO_NOTHING, blank=True, null=True)
+    title = models.CharField(max_length=255, blank=True, null=True)
+    description = models.CharField(max_length=255, blank=True, null=True)
+    created_at = models.DateTimeField(blank=True, null=True)
+    updated_at = models.DateTimeField(blank=True, null=True)
+    is_active = models.IntegerField(blank=True, null=True)
+    form_json = models.TextField(db_column='form_JSON', blank=True, null=True)  # Field name made lowercase.
+    def __str__(self):
+        return str(self.title)
+    

### 2023-03-15 django/CS476P/CS476P/users/views.py
Update views.py

@@ -87,6 +87,12 @@ def userAccount(request):
     return render(request, 'users/account.html', context)
 
 
+def tests(request):
+    tests = Test.objects.all()
+    context = {'tests':tests}
+    return render (request, 'users/test.html', context)
+
+
 @login_required
 def formEditor(request):
     return render(request, 'users/formEditor.html')

### 2023-03-16 django/dLocal/dLocal/projects/views.py
passed the formJSON to survery.html

@@ -45,13 +45,14 @@ def survey(request):
     return render(request, 'projects/Survey.html')
 
 def survey(request, form_id):
-    # form = Forms.objects.get(id=form_id)
-    # form_JSON = form.form_json
+    form = Forms.objects.get(form_id=form_id)
+    form_JSON = form.form_json
+    print(form_JSON)
     # form_titles = form.title
     
     # Do any additional processing or rendering here
     # return render(request, 'survey.html', {'form': form})
-    return render(request, 'projects/Survey.html', {'form_id': form_id})
+    return render(request, 'projects/Survey.html', {'form_id': form_id, 'form_JSON': form_JSON})
 
 def thanks(request):
     return render(request, 'projects/Thanks.html')

### 2023-03-16 django/dLocal/dLocal/static/js/survey.js

@@ -346,8 +346,19 @@ function sendData() {
 
 
 
+// wait for the DOM to finish loading
+document.addEventListener('DOMContentLoaded', (event) => {
+    console.log("this should show up");
+    console.log(document.getElementById("formJSON").innerHTML);
+    testJSON = [{"formTitle":"aaaa-"},{"inputID":"inputContainer0","fieldType":"text-field","fieldNameQuestion":"asdasda"},{"inputID":"inputContainer1","fieldType":"attitude-scale","fieldNameQuestion":"weee"},{"inputID":"inputContainer2","fieldType":"text-field","fieldNameQuestion":"tttt"},{"inputID":"inputContainer3","fieldType":"true-false","fieldNameQuestion":"aaaa"},{"inputID":"inputContainer4","fieldType":"text-field","fieldNameQuestion":"aaaa"}]
+    testJSON = [{"formTitle":"asdasd11212"},{"inputID":"inputContainer0","fieldType":"text-field","fieldNameQuestion":"wwww"},{"inputID":"inputContainer1","fieldType":"text-field","fieldNameQuestion":"aaaa"},{"inputID":"inputContainer2","fieldType":"text-field","fieldNameQuestion":"zzzz"}]
 
-testJSON = [{"formTitle":"Form1Test"},{"inputID":"inputContainer0","fieldType":"text-field","fieldNameQuestion":"text field test"},{"inputID":"inputContainer1","fieldType":"attitude-scale","fieldNameQuestion":"Did you have a good day?"},{"inputID":"inputContainer2","fieldType":"true-false","fieldNameQuestion":"true false"},{"inputID":"inputContainer3","fieldType":"text-field","fieldNameQuestion":""}]
+    loadFormUser(testJSON);
+  })
+    
+
+testJSON = document.getElementById("formJSON").innerHTML;
+
 // testJSON = [{"formTitle":"-Name your form here!-"},{"inputID":"inputContainer0","fieldType":"text-field","fieldNameQuestion":"asdasda"},{"inputID":"inputContainer1","fieldType":"attitude-scale","fieldNameQuestion":"weee"},{"inputID":"inputContainer2","fieldType":"text-field","fieldNameQuestion":"tttt"},{"inputID":"inputContainer3","fieldType":"true-false","fieldNameQuestion":"aaaa"},{"inputID":"inputContainer4","fieldType":"text-field","fieldNameQuestion":"aaaa"}]
 
[…]

### 2023-03-16 django/dLocal/dLocal/static/js/survey.js
Fixed survey showing wrong questions
Surveys now show the correct survey information.

@@ -349,11 +349,16 @@ function sendData() {
 // wait for the DOM to finish loading
 document.addEventListener('DOMContentLoaded', (event) => {
     console.log("this should show up");
-    console.log(document.getElementById("formJSON").innerHTML);
-    testJSON = [{"formTitle":"aaaa-"},{"inputID":"inputContainer0","fieldType":"text-field","fieldNameQuestion":"asdasda"},{"inputID":"inputContainer1","fieldType":"attitude-scale","fieldNameQuestion":"weee"},{"inputID":"inputContainer2","fieldType":"text-field","fieldNameQuestion":"tttt"},{"inputID":"inputContainer3","fieldType":"true-false","fieldNameQuestion":"aaaa"},{"inputID":"inputContainer4","fieldType":"text-field","fieldNameQuestion":"aaaa"}]
-    testJSON = [{"formTitle":"asdasd11212"},{"inputID":"inputContainer0","fieldType":"text-field","fieldNameQuestion":"wwww"},{"inputID":"inputContainer1","fieldType":"text-field","fieldNameQuestion":"aaaa"},{"inputID":"inputContainer2","fieldType":"text-field","fieldNameQuestion":"zzzz"}]
 
-    loadFormUser(testJSON);
+    var testJSON = document.getElementById("formJSON").innerHTML;
+
+    // console.log(testJSON);
+    console.log(JSON.parse(testJSON));
+
+    // testJSON = [{"formTitle":"aaaa-"},{"inputID":"inputContainer0","fieldType":"text-field","fieldNameQuestion":"asdasda"},{"inputID":"inputContainer1","fieldType":"attitude-scale","fieldNameQuestion":"weee"},{"inputID":"inputContainer2","fieldType":"text-field","fieldNameQuestion":"tttt"},{"inputID":"inputContainer3","fieldType":"true-false","fieldNameQuestion":"aaaa"},{"inputID":"inputContainer4","fieldType":"text-field","fieldNameQuestion":"aaaa"}]
+    // testJSON = [{"formTitle":"asdasd11212"},{"inputID":"inputContainer0","fieldType":"text-field","fieldNameQuestion":"wwww"},{"inputID":"inputContainer1","fieldType":"text-field","fieldNameQuestion":"aaaa"},{"inputID":"inputContainer2","fieldType":"text-field","fieldNameQuestion":"zzzz"}]
+
+    loadFormUser(JSON.parse(testJSON));
   })
     
 

### 2023-03-16 django/dLocal/dLocal/projects/models.py
Updates on sending response data to database

@@ -91,3 +91,17 @@ class Forms(models.Model):
     class Meta:
         managed = False
         db_table = 'forms'
+        
+        
+class Responses(models.Model):
+    response_id = models.AutoField(primary_key=True)
+    form = models.ForeignKey(Forms, models.DO_NOTHING, blank=True, null=True)
+    user = models.IntegerField(blank=True, null=True) 
+    # user = models.ForeignKey('Users', models.DO_NOTHING, blank=True, null=True)
+    response_json = models.TextField(db_column='response_JSON', blank=True, null=True)  # Field name made lowercase.
+    created_at = models.DateTimeField(blank=True, null=True)
+    updated_at = models.DateTimeField(blank=True, null=True)
+
+    class Meta:
+        managed = False
+        db_table = 'responses'

### 2023-03-16 django/dLocal/dLocal/projects/views.py

@@ -12,6 +12,7 @@ from django.contrib import messages
 
 from users.models import User
 from projects.models import Forms
+from projects.models import Responses
 
 # Create your views here.
 
@@ -47,7 +48,7 @@ def survey(request):
 def survey(request, form_id):
     form = Forms.objects.get(form_id=form_id)
     form_JSON = form.form_json
-    print(form_JSON)
+    # print(form_JSON)
     # form_titles = form.title
     
     # Do any additional processing or rendering here
@@ -96,3 +97,25 @@ def saveFormEditor(request):
             return JsonResponse({'status': 'error', 'message': 'Invalid request method'})
     else:
         return JsonResponse({'status': 'error', 'message': 'User is not authenticated'})
+    
+    
+    
+def saveResponses(request):   
+    # return render(request, 'projects/saveFormEditor.html')
+    # if request.user.is_authenticated:
+    if request.method == 'POST':
+        json_data = request.body.decode('utf-8')  # decode the request body
+        # user_id = request.user.id
+        
+        print(json_data)
+        
+        # get the form title from the JSON data
+        newFormTitle = list(json.loads(json_data)[0].values())[0]
+        
+        response = Responses(response_json=json_data, user='1')  # create a Form object with the JSON data
+        response.save()  # save the Form object to the database
+        return JsonResponse({'status': 'ok'})
+    else:
+        return JsonResponse({'status': 'error', 'message': 'Invalid request method'})
+    # else:
+    #     return JsonResponse({'status': 'error', 'message': 'User is not authenticated'})

### 2023-03-16 django/dLocal/dLocal/static/js/survey.js

@@ -300,8 +300,8 @@ function submitResponses(){
             responseValue: responseValue
         });
     }
-    console.log(responseJSON);
-    document.getElementById("responseJSON").innerHTML = "Response JSON: <br>" + JSON.stringify(responseJSON);
+    // console.log(responseJSON);
+    // document.getElementById("responseJSON").innerHTML = "Response JSON: <br>" + JSON.stringify(responseJSON);
     return responseJSON;
 }
 
@@ -324,13 +324,16 @@ function getCookie(name) {
 const csrftoken = getCookie('csrftoken');
 
 function sendData() {
-    var myVariable = saveForm();
-    fetch('/../saveFormEditor/', {
+    console.log("sendData() called");
+
+    var myVariable = submitResponses();
+    fetch('/../saveResponses/', {
     method: 'POST',
     headers: {
         'Content-Type': 'application/json',
         'X-CSRFToken': csrftoken
     },
+    // need to pass JSON, dateTime, and formID !!!!!!!!!!!!!
     body: JSON.stringify(myVariable)
     })
     .then(response => {
@@ -348,12 +351,12 @@ function sendData() {
 
 // wait for the DOM to finish loading
 document.addEventListener('DOMContentLoaded', (event) => {
-    console.log("this should show up");
+    // console.log("this should show up");
 
     var testJSON = document.getElementById("formJSON").innerHTML;
 
     // console.log(testJSON);
-    console.log(JSON.parse(testJSON));
+    // console.log(JSON.parse(testJSON));
 
     // testJSON = [{"formTitle":"aaaa-"},{"inputID":"inputContainer0","fieldType":"text-field","fieldNameQuestion":"asdasda"},{"inputID":"inputContainer1","fieldType":"attitude-scale","fieldNameQuestion":"weee"},{"inputID":"inputContainer2","fieldType":"text-field","fieldNameQuestion":"tttt"},{"inputID":"inputContainer3","fieldType":"true-false","fieldNameQuestion":"aaaa"},{"inputID":"inputContainer4","fieldType":"text-field","fieldNameQuestion":"aaaa"}]
     // testJSON = [{"formTitle":"asdasd11212"},{"inputID":"inputContainer0","fieldType":"text-field","fieldNameQuestion":"wwww"},{"inputID":"inputContainer1","fieldType":"text-field","fieldNameQuestion":"aaaa"},{"inputID":"inputContainer2","fieldType":"text-field","fieldNameQuestion":"zzzz"}]

### 2023-03-16 paper/main.tex
Updated paper to include new info

@@
 \hfill \break
+\newpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\newpage 
 \section{Top-level and Low-level Software Design}
 \subsection{Provide the MVC architecture according to the selected Web frame- work. Also, describe at least three benefits of MVC for your application.}
-\linebreak
-    \hfill \break
+\newline
+\hfill
+
+Django uses MVT (Model View Template) architecture which is a variation of the traditional MVC (Model View Controller) architecture.
+Similar to the MVC, the Model in MVT represents the data and the business logic.
+The View in MVT is split into two parts.
+The Template displays the data while the View handles the user input and interacts with the Model to retrieve and manipulate the data.
+Similar to the MVC, MVT separates layers and keeps the code organized and maintainable while also simplifying the View by separating it into two parts.
+\newline
+
+The MVT architecture allows the developer to work on each layer in parallel and then integrate them efficiently.
+In our project, we used this feature to build and test the three main functions: user authentication process, creation of surveys by the feedback gatherers, and submission of surveys by the respondents.
+\newline
+
+For the user registration and authentication processes, we first created the template for the user to register and log in, and the table in the model to store the user information data.
+Views were then set up to handle the user input and to retrieve and manipulate the data.
+Finally, the template was finalized to display the data.
+\newpage
 
@@
 \begin{enumerate}
-   \item thing
+   \item  Django web and database frameworks:
    \begin{description}
-     \item description
+     \item \url{https://docs.djangoproject.com/en/4.1/}
    \end{description}
@@
 \begin{enumerate}
-   \item React
+   \item Django
    \begin{description}
-     \item description
+     \item The main functionality of our web application requires a web framework with a database that can be used to store and load user’s data such as their surveys and responses.
+Django allows quick and efficient development of our web application by providing the framework and the modules.
+The nuisance of creating and connecting to a database is already implemented in Django.
+We were able to quickly test the storage and loading of our data in the early stages of development.
+Migration of our data was also made simple by Django because it only requires running a few commands in the terminal.
    \end{description}
-   \item Django
+   \item ngrok
+   \item mySQL
 \end{enumerate}
@@
 \subsection{Correctness testing using four test cases (screenshots of both inputs and outputs).}
+\newline
+\hfill
+
+\textbf{Feedback gatherer:}
+\begin{itemize}
+    \item[] Input: Feedback gatherer creates a survey by selecting the types of answers and entering the questions. 
+    \item[] Output: When they click the “Create Survey” button, a QR code is generated.
+    \item[] Input: Feedback gatherer scans the QR code.
+    \item[] Output: Feedback gatherer is taken to the correct survey displaying the correct questions.
+    \item[] Input: Feedback gatherer clicks on one of the past surveys.
+    \item[] Output: Feedback gatherer can view the responses.
+    \item[] Input: Feedback gatherer clicks the delete button on one of the past surveys.
+    \item[] Output: The past survey is deleted.
+\end{itemize}
+
+\hfill \break
+\textbf{Respondent:}
+\begin{itemize}
+    \item[] Input: Respondent scans the QR code.
+    \item[] Output: Respondent is taken to the correct survey.
+    \item[] Input: Respondent completes the survey and clicks submit.
+    \item[] Output: Respondent is taken to the thank you page.
+\end{itemize}
+
+\hfill \break
+\newpage
+
 \subsection{Robustness testing using four test cases (screenshots of both inputs and outputs).}
+\newline
+\hfill
+
+\textbf{Feedback gatherer:}
+
+\begin{itemize}
+    \item[] Input: Feedback gatherer clicks the “Create Survey” button without entering anything.
+\item[] Output: Feedback gatherer is shown a warning to select a type of answer and to enter a question.
+\item[] Input: Feedback gatherer clicks the “Create Survey” button without entering a question after selecting a type of answer.
+\item[] Output: Feedback gatherer is shown a warning to enter a question.
+\item[] Input: Feedback gatherer attempts to close the browser or to return to the main page while creating a survey.
+\item[] Output: Feedback gatherer is shown a warning that the entered information will be lost.
+\end{itemize}
+\newline 
+\hfill \break
+
+\textbf{Respondent:}
+\begin{itemize}
+    \item[] Input: Respondent clicks the submit button without answering all of the questions.
+
+Output: Respondent is shown a warning to answer all of the questions.
+
+Input: Respondent attempts to leave the survey without submitting.
+
+Output: Respondent is shown a warning that the entered information will be lost.
+
+\end{itemize}
+\newpage
+
 \subsection{Time-eﬀiciency testing of two functions (with screenshots). Indicate the method you used to measure the time.}
+\newline
+\hfill \break
+
+\textbf{Feedback gatherer:}
+\begin{itemize}
+    \item[] Create survey: Time taken for the survey data to be stored in the database and the QR code to be generated.
+
+View responses: Time taken for the response data to be shown to the feedback gatherer after clicking a past survey. 
+\end{itemize}
+\newline
+\hfill \break
+
+\textbf{Respondent:}
+\begin{itemize}
+    \item[] Go to survey: Time taken for the survey to be loaded from the database when the QR code is scanned.
+
+Submit responses: Time taken for the response data to be stored in the database and to show the respondent that the responses were successfully submitted.
+\end{itemize}
 

### 2023-03-16 django/dLocal/dLocal/projects/models.py
Reponses are now saved in database

@@ -96,7 +96,7 @@ class Forms(models.Model):
 class Responses(models.Model):
     response_id = models.AutoField(primary_key=True)
     form = models.ForeignKey(Forms, models.DO_NOTHING, blank=True, null=True)
-    user = models.IntegerField(blank=True, null=True) 
+    user_id = models.IntegerField(blank=True, null=True) 
     # user = models.ForeignKey('Users', models.DO_NOTHING, blank=True, null=True)
     response_json = models.TextField(db_column='response_JSON', blank=True, null=True)  # Field name made lowercase.
     created_at = models.DateTimeField(blank=True, null=True)

### 2023-03-16 django/dLocal/dLocal/projects/urls.py

@@ -14,4 +14,5 @@ urlpatterns = [
     path('thanks/', views.thanks, name="thanks"),
     path('formEditor/', views.formEditor, name="formEditor"),
     path('saveFormEditor/', views.saveFormEditor, name="saveFormEditor"),
+    path('saveResponses/', views.saveResponses, name="saveResponses"),
 ]

### 2023-03-16 django/dLocal/dLocal/projects/views.py

@@ -107,12 +107,22 @@ def saveResponses(request):
         json_data = request.body.decode('utf-8')  # decode the request body
         # user_id = request.user.id
         
-        print(json_data)
+        json_data = list(json.loads(json_data).values())
+        
+        responseDate = json_data[0]
+        responseFormID = json_data[1]
+        responseJSON = json_data[2]
+        
+        # print the 3 vars above
+        print(responseJSON)
+        print(responseDate)
+        print(responseFormID)
         
         # get the form title from the JSON data
-        newFormTitle = list(json.loads(json_data)[0].values())[0]
         
-        response = Responses(response_json=json_data, user='1')  # create a Form object with the JSON data
+        # newFormTitle = list(json.loads(json_data)[0].values())[0]
+        
+        response = Responses(response_json=responseJSON, created_at=responseDate, form_id=responseFormID)  # create a Form object with the JSON data
         response.save()  # save the Form object to the database
         return JsonResponse({'status': 'ok'})
     else:

### 2023-03-16 django/dLocal/dLocal/static/js/survey.js

@@ -324,9 +324,21 @@ function getCookie(name) {
 const csrftoken = getCookie('csrftoken');
 
 function sendData() {
-    console.log("sendData() called");
+    // console.log("sendData() called");
 
+    formID = document.getElementById("formNumber").innerHTML;
     var myVariable = submitResponses();
+    myVariable = JSON.stringify(myVariable);
+
+    // get data time with native JS
+    var dateTime = new Date().toISOString().slice(0, 19).replace('T', ' ');
+    console.log(dateTime);
+
+    // put data into JSON
+    var bodyData = JSON.stringify({ "dateTime": dateTime, "formID": formID, "responseJSON": myVariable });
+
+    console.log(bodyData);
+    
     fetch('/../saveResponses/', {
     method: 'POST',
     headers: {
@@ -334,7 +346,9 @@ function sendData() {
         'X-CSRFToken': csrftoken
     },
     // need to pass JSON, dateTime, and formID !!!!!!!!!!!!!
-    body: JSON.stringify(myVariable)
+    
+
+    body: bodyData
     })
     .then(response => {
     // Handle the response from the Django view
@@ -347,7 +361,7 @@ function sendData() {
 
 }
 
-
+// console.log("this should show up");
 
 // wait for the DOM to finish loading
 document.addEventListener('DOMContentLoaded', (event) => {

### 2023-03-17 django/dLocal/dLocal/CS476P/settings.py
fixed the QR code generated URLs

@@ -26,9 +26,9 @@ SECRET_KEY = 'django-insecure-m$!7d!!7*kf3#ii&w9*6pk%-6i62#%ngn1fic6iz$3!(^m_ud%
 # SECURITY WARNING: don't run with debug turned on in production!
 DEBUG = True
 
-ALLOWED_HOSTS = ['localhost', '127.0.0.1', '0.0.0.0', 'a026-67-225-4-188.ngrok.io']
+ALLOWED_HOSTS = ['localhost', '127.0.0.1', '0.0.0.0', 'a026-67-225-4-188.ngrok.io', 'b62d-67-225-4-188.ngrok.io', 'commentcorner.ngrok.app']
 
-CSRF_TRUSTED_ORIGINS = ['https://8994-67-225-4-188.ngrok.io']
+CSRF_TRUSTED_ORIGINS = ['https://8994-67-225-4-188.ngrok.io', 'https://b62d-67-225-4-188.ngrok.io', 'https://commentcorner.ngrok.app']
 
 # Application definition
 

### 2023-03-17 django/dLocal/dLocal/CS476P/urls.py

@@ -24,6 +24,7 @@ urlpatterns = [
     path('admin/', admin.site.urls),
     path('', include('projects.urls')),
     path('users/', include('users.urls')),
+    
 ]
 
 urlpatterns += static(settings.MEDIA_URL, document_root=settings.MEDIA_ROOT)

### 2023-03-17 django/dLocal/dLocal/projects/urls.py

@@ -10,7 +10,7 @@ urlpatterns = [
     path('QRcode/', views.QRcode, name="QRcode"),
     path('signup/', views.signup, name="signup"),
     path('survey/', views.survey, name="survey"),
-    path('survey/<int:form_id>', views.survey, name="survey"),
+    path('survey/<int:form_id>/', views.survey, name="survey"),
     path('thanks/', views.thanks, name="thanks"),
     path('formEditor/', views.formEditor, name="formEditor"),
     path('saveFormEditor/', views.saveFormEditor, name="saveFormEditor"),

### 2023-03-17 django/dLocal/dLocal/projects/urls.py
Added results page and results logic

@@ -15,4 +15,6 @@ urlpatterns = [
     path('formEditor/', views.formEditor, name="formEditor"),
     path('saveFormEditor/', views.saveFormEditor, name="saveFormEditor"),
     path('saveResponses/', views.saveResponses, name="saveResponses"),
+    path('results/', views.results, name="results"),
+    path('results/<int:form_id>/', views.results, name="results"),
 ]

### 2023-03-17 django/dLocal/dLocal/projects/views.py

@@ -14,6 +14,8 @@ from users.models import User
 from projects.models import Forms
 from projects.models import Responses
 
+
+import pandas as pd
 # Create your views here.
 
 def home(request):
@@ -99,7 +101,6 @@ def saveFormEditor(request):
         return JsonResponse({'status': 'error', 'message': 'User is not authenticated'})
     
     
-    
 def saveResponses(request):   
     # return render(request, 'projects/saveFormEditor.html')
     # if request.user.is_authenticated:
@@ -129,3 +130,43 @@ def saveResponses(request):
         return JsonResponse({'status': 'error', 'message': 'Invalid request method'})
     # else:
     #     return JsonResponse({'status': 'error', 'message': 'User is not authenticated'})
+    
+    
+def results(request, form_id):
+    results = Responses.objects.filter(form_id=form_id)
+    
+    # Create a list of all the response JSONs
+    newList = []
+    for responseObject in results:
+        response_list = json.loads(responseObject.response_json)
+        for list in response_list:
+            newList.append(list)
+        
+    # Create a dictionary of unique responseHeadings and values
+    response_dict = {}
+    for item in newList:
+        heading = item['responseHeading']
+        value = item['responseValue'].strip()
+        if heading not in response_dict:
+            response_dict[heading] = [value]
+        else: # value not in response_dict[heading]:
+            response_dict[heading].append(value)
+
+    # Print the resulting dictionary
+    # print(response_dict)
+    
+    # convert a dictionary into a dataframe
+    
+    df = pd.DataFrame(response_dict)
+    # print(df)
+    
+    results_table = df.to_html()
+    # print(results_table)
+   
+    
+    # return render(request, 'survey.html', {'form': form})
+    return render(request, 'projects/results.html', {'form_id': form_id, 'results_table': results_table})
+
+
+def thanks(request):
+    return render(request, 'projects/Thanks.html')

### 2023-03-17 django/dLocal/dLocal/projects/views.py
Removed index column from results table

@@ -158,9 +158,12 @@ def results(request, form_id):
     # convert a dictionary into a dataframe
     
     df = pd.DataFrame(response_dict)
-    # print(df)
     
-    results_table = df.to_html()
+    # remove index column
+    df =  df.reset_index(drop=True)
+    print(df)
+    
+    results_table = df.to_html(index=False)
     # print(results_table)
    
     

### 2023-03-17 django/dLocal/dLocal/projects/views.py
fixed bug with true/false results

@@ -146,7 +146,10 @@ def results(request, form_id):
     response_dict = {}
     for item in newList:
         heading = item['responseHeading']
-        value = item['responseValue'].strip()
+        value = item['responseValue']
+        if isinstance(value, str):
+            value = item['responseValue'].strip()
+        
         if heading not in response_dict:
             response_dict[heading] = [value]
         else: # value not in response_dict[heading]:

### 2023-03-17 django/dLocal/dLocal/static/js/survey.js

@@ -299,6 +299,8 @@ function submitResponses(){
             responseHeading: responseHeading,
             responseValue: responseValue
         });
+
+        console.log(typeof responseValue);
     }
     // console.log(responseJSON);
     // document.getElementById("responseJSON").innerHTML = "Response JSON: <br>" + JSON.stringify(responseJSON);

### 2023-03-17 django/dLocal/dLocal/static/js/survey.js
Fixed attitude-scale results bug

@@ -231,27 +231,27 @@ function addResponseElement(inputType, questionHeading){
         case "attitude-scale":
             var newInput = createInputElement("radio");
             newInput.setAttribute("name", "attitude-scale" + responseInputs);
-            newInput.setAttribute("value", "1");
+            newInput.setAttribute("value", "Disagree");
             newInput.setAttribute("checked", "checked");
             newDiv.appendChild(newInput);
             var newLabel = document.createElement("label");
-            newLabel.setAttribute("for", "1");
+            newLabel.setAttribute("for", "Disagree");
             newLabel.innerHTML = "1 = Disagree";
             newDiv.appendChild(newLabel);
             var newInput = createInputElement("radio");
             newInput.setAttribute("name", "attitude-scale" + responseInputs);
-            newInput.setAttribute("value", "2");
+            newInput.setAttribute("value", "Neutral");
             newDiv.appendChild(newInput);
             var newLabel = document.createElement("label");
-            newLabel.setAttribute("for", "2");
+            newLabel.setAttribute("for", "Neutral");
             newLabel.innerHTML = "2 = Neutral";
             newDiv.appendChild(newLabel);
             var newInput = createInputElement("radio");
             newInput.setAttribute("name", "attitude-scale" + responseInputs);
-            newInput.setAttribute("value", "3");
+            newInput.setAttribute("value", "Agree");
             newDiv.appendChild(newInput);
             var newLabel = document.createElement("label");
-            newLabel.setAttribute("for", "3");
+            newLabel.setAttribute("for", "Agree");
             newLabel.innerHTML = "3 = Agree";
             newDiv.appendChild(newLabel);
             break;
@@ -292,9 +292,9 @@ function submitResponses(){
         var responseHeading = child.children[0].innerHTML;
         var responseInput = child.children[1];
         var responseValue = responseInput.value;
-        if(responseInput.type == "radio"){
-            responseValue = responseInput.checked;
-        }
+        // if(responseInput.type == "radio"){
+        //     responseValue = responseInput.checked;
+        // }
         responseJSON.push({
             responseHeading: responseHeading,
             responseValue: responseValue

### 2023-03-17 django/dLocal/dLocal/projects/views.py
Added permission check for results page

@@ -14,9 +14,8 @@ from users.models import User
 from projects.models import Forms
 from projects.models import Responses
 
-
 import pandas as pd
-# Create your views here.
+
 
 def home(request):
     # projects = Project.objects.all()
@@ -50,11 +49,6 @@ def survey(request):
 def survey(request, form_id):
     form = Forms.objects.get(form_id=form_id)
     form_JSON = form.form_json
-    # print(form_JSON)
-    # form_titles = form.title
-    
-    # Do any additional processing or rendering here
-    # return render(request, 'survey.html', {'form': form})
     return render(request, 'projects/Survey.html', {'form_id': form_id, 'form_JSON': form_JSON})
 
 def thanks(request):
@@ -64,21 +58,6 @@ def thanks(request):
 @login_required
 def formEditor(request):
     return render(request, 'projects/formEditor.html')
-    # if request.method == 'POST':
-        
-    #     my_variable = request.POST.get('myVariable', None)
-    #     user_id = request.user.id
-    #     try:
-    #         json_data = json.loads(my_variable)
-    #     except ValueError:
-    #         return JsonResponse({'status': 'error', 'message': 'Invalid JSON data'})
-    #     form = Form(user_id=user_id, json_data=json_data)
-    #     form.save()
-    #     return JsonResponse({'status': 'ok'})
-    #     return HttpResponse('Form submitted')
-    # else:
-    #     render(request, 'projects/formEditor.html')
-    #     return HttpResponse('Form submitted')
     
     
 @login_required
@@ -100,7 +79,8 @@ def saveFormEditor(request):
     else:
         return JsonResponse({'status': 'error', 'message': 'User is not authenticated'})
     
-    
+
+
 def saveResponses(request):   
     # return render(request, 'projects/saveFormEditor.html')
     # if request.user.is_authenticated:
@@ -119,60 +99,54 @@ def saveResponses(request):
         print(responseDate)
         print(responseFormID)
         
-        # get the form title from the JSON data
-        
-        # newFormTitle = list(json.loads(json_data)[0].values())[0]
-        
         response = Responses(response_json=responseJSON, created_at=responseDate, form_id=responseFormID)  # create a Form object with the JSON data
         response.save()  # save the Form object to the database
         return JsonResponse({'status': 'ok'})
     else:
         return JsonResponse({'status': 'error', 'message': 'Invalid request method'})
-    # else:
[…]

### 2023-03-20 django/CS476P/CS476P/CS476P/asgi.py
deleted / refactored code

@@ -1,16 +1,0 @@
-"""
-ASGI config for CS476P project.
-
-It exposes the ASGI callable as a module-level variable named ``application``.
-
-For more information on this file, see
-https://docs.djangoproject.com/en/4.1/howto/deployment/asgi/
-"""
-
-import os
-
-from django.core.asgi import get_asgi_application
-
-os.environ.setdefault('DJANGO_SETTINGS_MODULE', 'CS476P.settings')
-
-application = get_asgi_application()

### 2023-03-20 django/CS476P/CS476P/CS476P/settings.py

@@ -1,142 +1,0 @@
-"""
-Django settings for CS476P project.
-
-Generated by 'django-admin startproject' using Django 4.1.7.
-
-For more information on this file, see
-https://docs.djangoproject.com/en/4.1/topics/settings/
-
-For the full list of settings and their values, see
-https://docs.djangoproject.com/en/4.1/ref/settings/
-"""
-
-from pathlib import Path
-import os
-
-# Build paths inside the project like this: BASE_DIR / 'subdir'.
-BASE_DIR = Path(__file__).resolve().parent.parent
-
-
-# Quick-start development settings - unsuitable for production
-# See https://docs.djangoproject.com/en/4.1/howto/deployment/checklist/
-
-# SECURITY WARNING: keep the secret key used in production secret!
-SECRET_KEY = 'django-insecure-m$!7d!!7*kf3#ii&w9*6pk%-6i62#%ngn1fic6iz$3!(^m_ud%'
-
-# SECURITY WARNING: don't run with debug turned on in production!
-DEBUG = True
-
-ALLOWED_HOSTS = ['localhost', '127.0.0.1']
-
-
-# Application definition
-
-INSTALLED_APPS = [
-    'django.contrib.admin',
-    'django.contrib.auth',
-    'django.contrib.contenttypes',
-    'django.contrib.sessions',
-    'django.contrib.messages',
-    'django.contrib.staticfiles',
-
-    'projects.apps.ProjectsConfig',
-    'users.apps.UsersConfig',
-]
-
-MIDDLEWARE = [
-    'django.middleware.security.SecurityMiddleware',
-
-    'whitenoise.middleware.WhiteNoiseMiddleware',
-
-    'django.contrib.sessions.middleware.SessionMiddleware',
-    'django.middleware.common.CommonMiddleware',
-    'django.middleware.csrf.CsrfViewMiddleware',
-    'django.contrib.auth.middleware.AuthenticationMiddleware',
-    'django.contrib.messages.middleware.MessageMiddleware',
-    'django.middleware.clickjacking.XFrameOptionsMiddleware',
-]
-
-ROOT_URLCONF = 'CS476P.urls'
-
-TEMPLATES = [
-    {
-        'BACKEND': 'django.template.backends.django.DjangoTemplates',
-        'DIRS': [
-            os.path.join(BASE_DIR, 'templates'),
-        ],
-        'APP_DIRS': True,
-        'OPTIONS': {
[…]

### 2023-03-20 django/CS476P/CS476P/CS476P/urls.py

@@ -1,30 +1,0 @@
-"""CS476P URL Configuration
-
-The `urlpatterns` list routes URLs to views. For more information please see:
-    https://docs.djangoproject.com/en/4.1/topics/http/urls/
-Examples:
-Function views
-    1. Add an import:  from my_app import views
-    2. Add a URL to urlpatterns:  path('', views.home, name='home')
-Class-based views
-    1. Add an import:  from other_app.views import Home
-    2. Add a URL to urlpatterns:  path('', Home.as_view(), name='home')
-Including another URLconf
-    1. Import the include() function: from django.urls import include, path
-    2. Add a URL to urlpatterns:  path('blog/', include('blog.urls'))
-"""
-from django.contrib import admin
-from django.urls import path, include
-
-
-from django.conf import settings
-from django.conf.urls.static import static
-
-urlpatterns = [
-    path('admin/', admin.site.urls),
-    path('', include('projects.urls')),
-    path('users/', include('users.urls')),
-]
-
-urlpatterns += static(settings.MEDIA_URL, document_root=settings.MEDIA_ROOT)
-urlpatterns += static(settings.STATIC_URL, document_root=settings.STATIC_ROOT)

### 2023-03-20 django/CS476P/CS476P/CS476P/wsgi.py

@@ -1,16 +1,0 @@
-"""
-WSGI config for CS476P project.
-
-It exposes the WSGI callable as a module-level variable named ``application``.
-
-For more information on this file, see
-https://docs.djangoproject.com/en/4.1/howto/deployment/wsgi/
-"""
-
-import os
-
-from django.core.wsgi import get_wsgi_application
-
-os.environ.setdefault('DJANGO_SETTINGS_MODULE', 'CS476P.settings')
-
-application = get_wsgi_application()

### 2023-03-20 django/CS476P/CS476P/manage.py

@@ -1,22 +1,0 @@
-#!/usr/bin/env python
-"""Django's command-line utility for administrative tasks."""
-import os
-import sys
-
-
-def main():
-    """Run administrative tasks."""
-    os.environ.setdefault('DJANGO_SETTINGS_MODULE', 'CS476P.settings')
-    try:
-        from django.core.management import execute_from_command_line
-    except ImportError as exc:
-        raise ImportError(
-            "Couldn't import Django. Are you sure it's installed and "
-            "available on your PYTHONPATH environment variable? Did you "
-            "forget to activate a virtual environment?"
-        ) from exc
-    execute_from_command_line(sys.argv)
-
-
-if __name__ == '__main__':
-    main()

### 2023-03-20 django/CS476P/CS476P/projects/admin.py

@@ -1,14 +1,0 @@
-from django.contrib import admin
-
-# Register your models here.
-
-from .models import Project, Review, Tag, Form, Response
-
-admin.site.register(Project)
-admin.site.register(Review)
-admin.site.register(Tag)
-
-
-
-admin.site.register(Form)
-admin.site.register(Response)

### 2023-03-20 django/CS476P/CS476P/projects/migrations/0001_initial.py

@@ -1,26 +1,0 @@
-# Generated by Django 4.1.7 on 2023-03-01 19:33
-
-from django.db import migrations, models
-import uuid
-
-
-class Migration(migrations.Migration):
-
-    initial = True
-
-    dependencies = [
-    ]
-
-    operations = [
-        migrations.CreateModel(
-            name='Project',
-            fields=[
-                ('title', models.CharField(max_length=200)),
-                ('description', models.TextField(blank=True, null=True)),
-                ('demo_link', models.CharField(blank=True, max_length=2000, null=True)),
-                ('source_link', models.CharField(blank=True, max_length=200, null=True)),
-                ('created', models.DateTimeField(auto_now_add=True)),
-                ('id', models.UUIDField(default=uuid.uuid4, editable=False, primary_key=True, serialize=False, unique=True)),
-            ],
-        ),
-    ]

### 2023-03-20 django/CS476P/CS476P/projects/migrations/0002_tag_project_vote_ratio_project_vote_total_review_and_more.py

@@ -1,48 +1,0 @@
-# Generated by Django 4.1.7 on 2023-03-01 22:33
-
-from django.db import migrations, models
-import django.db.models.deletion
-import uuid
-
-
-class Migration(migrations.Migration):
-
-    dependencies = [
-        ('projects', '0001_initial'),
-    ]
-
-    operations = [
-        migrations.CreateModel(
-            name='Tag',
-            fields=[
-                ('name', models.CharField(max_length=200)),
-                ('created', models.DateTimeField(auto_now_add=True)),
-                ('id', models.UUIDField(default=uuid.uuid4, editable=False, primary_key=True, serialize=False, unique=True)),
-            ],
-        ),
-        migrations.AddField(
-            model_name='project',
-            name='vote_ratio',
-            field=models.IntegerField(blank=True, default=0, null=True),
-        ),
-        migrations.AddField(
-            model_name='project',
-            name='vote_total',
-            field=models.IntegerField(blank=True, default=0, null=True),
-        ),
-        migrations.CreateModel(
-            name='Review',
-            fields=[
-                ('body', models.TextField(blank=True, null=True)),
-                ('value', models.CharField(choices=[('up', 'Up Vote'), ('down', 'Down Vote')], max_length=200)),
-                ('created', models.DateTimeField(auto_now_add=True)),
-                ('id', models.UUIDField(default=uuid.uuid4, editable=False, primary_key=True, serialize=False, unique=True)),
-                ('project', models.ForeignKey(on_delete=django.db.models.deletion.CASCADE, to='projects.project')),
-            ],
-        ),
-        migrations.AddField(
-            model_name='project',
-            name='tags',
-            field=models.ManyToManyField(blank=True, to='projects.tag'),
-        ),
-    ]

### 2023-03-20 django/CS476P/CS476P/projects/migrations/0003_form_project_featured_image_response.py

@@ -1,38 +1,0 @@
-# Generated by Django 4.1.7 on 2023-03-02 00:59
-
-from django.db import migrations, models
-import django.db.models.deletion
-import uuid
-
-
-class Migration(migrations.Migration):
-
-    dependencies = [
-        ('projects', '0002_tag_project_vote_ratio_project_vote_total_review_and_more'),
-    ]
-
-    operations = [
-        migrations.CreateModel(
-            name='Form',
-            fields=[
-                ('id', models.UUIDField(default=uuid.uuid4, editable=False, primary_key=True, serialize=False, unique=True)),
-                ('created', models.DateTimeField(auto_now_add=True)),
-                ('title', models.CharField(max_length=200)),
-                ('description', models.TextField(blank=True, null=True)),
-            ],
-        ),
-        migrations.AddField(
-            model_name='project',
-            name='featured_image',
-            field=models.ImageField(blank=True, default='default.jpg', null=True, upload_to=''),
-        ),
-        migrations.CreateModel(
-            name='Response',
-            fields=[
-                ('id', models.UUIDField(default=uuid.uuid4, editable=False, primary_key=True, serialize=False, unique=True)),
-                ('created', models.DateTimeField(auto_now_add=True)),
-                ('response_text', models.TextField(blank=True, null=True)),
-                ('form', models.ForeignKey(on_delete=django.db.models.deletion.CASCADE, to='projects.form')),
-            ],
-        ),
-    ]

### 2023-03-20 django/CS476P/CS476P/projects/migrations/0004_project_owner.py

@@ -1,20 +1,0 @@
-# Generated by Django 4.1.7 on 2023-03-02 02:45
-
-from django.db import migrations, models
-import django.db.models.deletion
-
-
-class Migration(migrations.Migration):
-
-    dependencies = [
-        ('users', '0002_profile_username'),
-        ('projects', '0003_form_project_featured_image_response'),
-    ]
-
-    operations = [
-        migrations.AddField(
-            model_name='project',
-            name='owner',
-            field=models.ForeignKey(blank=True, null=True, on_delete=django.db.models.deletion.SET_NULL, to='users.profile'),
-        ),
-    ]

### 2023-03-20 django/CS476P/CS476P/projects/models.py

@@ -1,65 +1,0 @@
-from django.db import models
-from django.contrib.auth.models import User
-import uuid
-from users.models import Profile
-
-# Create your models here.
-
-class Project(models.Model):
-    owner = models.ForeignKey(Profile, null=True, blank=True, on_delete=models.SET_NULL)
-    title = models.CharField(max_length=200)
-    description = models.TextField(null=True,blank=True)
-    featured_image = models.ImageField(null=True,blank=True,default="default.jpg")
-    demo_link = models.CharField(max_length=2000,blank=True,null=True)
-    source_link = models.CharField(max_length=200, blank=True,null=True)
-    tags = models.ManyToManyField('Tag', blank=True)
-    vote_total = models.IntegerField(default=0, null=True,blank=True)
-    vote_ratio = models.IntegerField(default=0, null=True,blank=True)
-    created = models.DateTimeField(auto_now_add=True)
-    id = models.UUIDField(default=uuid.uuid4,unique=True,primary_key=True,editable=False)
-
-    def __str__(self):
-        return self.title
-
-class Review(models.Model):
-    VOTE_TYPE = (
-        ('up', 'Up Vote'),
-        ('down', 'Down Vote'),
-    )
-    #owner =
-    project = models.ForeignKey(Project, on_delete=models.CASCADE)
-    body = models.TextField(null=True,blank=True)
-    value = models.CharField(max_length=200, choices = VOTE_TYPE)
-    created = models.DateTimeField(auto_now_add=True)
-    id = models.UUIDField(default=uuid.uuid4,unique=True,primary_key=True,editable=False)
-
-    def __str__(self):
-        return self.value
-    
-class Tag(models.Model):
-    name = models.CharField(max_length=200)
-    created = models.DateTimeField(auto_now_add=True)
-    id = models.UUIDField(default=uuid.uuid4,unique=True,primary_key=True,editable=False)
-
-    def __str__(self):
-        return self.name
-    
-
-
-
-
-class Form(models.Model):
-    id = models.UUIDField(default=uuid.uuid4,unique=True,primary_key=True,editable=False)
-    created = models.DateTimeField(auto_now_add=True)
-    title = models.CharField(max_length=200)
-    description = models.TextField(null=True,blank=True)
-    def __str__(self):
-        return self.title
-
-class Response(models.Model):
-    form = models.ForeignKey(Form, on_delete=models.CASCADE)
[…]

### 2023-03-20 django/CS476P/CS476P/projects/urls.py

@@ -1,14 +1,0 @@
-from django.urls import path
-from . import views
-
-urlpatterns = [
-    path('', views.home, name="home"),
-    path('createsurvey/', views.createsurvey, name="createsurvey"),
-    path('landingpage/', views.landingpage, name="landingpage"),
-    path('login/', views.login, name="login"),
-    path('profile/', views.profile, name="profile"),
-    path('QRcode/', views.QRcode, name="QRcode"),
-    path('signup/', views.signup, name="signup"),
-    path('survey/', views.survey, name="survey"),
-    path('thanks/', views.thanks, name="thanks"),
-]

### 2023-03-20 django/CS476P/CS476P/projects/views.py

@@ -1,42 +1,0 @@
-from django.shortcuts import render, redirect
-from django.contrib.auth import login, authenticate, logout
-from django.contrib.auth.models import User
-from django.urls import path
-from .models import Project
-from django.contrib.auth.decorators import login_required
-
-# Create your views here.
-
-def home(request):
-    # projects = Project.objects.all()
-    # context = { 'projects':projects}
-    return render(request, 'projects/Home.html')
-
-@login_required(login_url='login')
-def createsurvey(request):
-    return render(request, 'projects/CreateSurvey.html')
-
-@login_required(login_url='login')
-def landingpage(request):
-    return render(request, 'projects/LandingPage.html')
-
-def login(request):
-    return render(request, 'projects/Login.html')
-
-@login_required(login_url='login')
-def profile(request):
-    return render(request, 'projects/Profile.html')
-
-def QRcode(request):
-    return render(request, 'projects/QRcode.html')
-
-def signup(request):
-    return render(request, 'projects/Signup.html')
-
-def survey(request):
-    return render(request, 'projects/Survey.html')
-
-def thanks(request):
-    return render(request, 'projects/Thanks.html')
-
-

### 2023-03-20 django/CS476P/CS476P/users/admin.py

@@ -1,8 +1,0 @@
-from django.contrib import admin
-
-# Register your models here.
-
-from .models import Profile, Skill
-
-admin.site.register(Profile)
-admin.site.register(Skill)

### 2023-03-20 django/CS476P/CS476P/users/forms.py

@@ -1,17 +1,0 @@
-from django.forms import ModelForm
-from django.contrib.auth.forms import UserCreationForm
-from django.contrib.auth.models import User
-
-class CustomUserCreationForm(UserCreationForm):
-    class Meta:
-        model = User
-        fields = ['first_name', 'email', 'username', 'password1', 'password2']
-        labels = {
-            'first_name':'Name',
-        }
-
-    def __init__(self, *args, **kwargs):
-        super(CustomUserCreationForm, self).__init__(*args, **kwargs)
-
-        for name, field in self.fields.items():
-            field.widget.attrs.update({'class': 'input'})

### 2023-03-20 django/CS476P/CS476P/users/migrations/0001_initial.py

@@ -1,35 +1,0 @@
-# Generated by Django 4.1.7 on 2023-03-02 02:39
-
-from django.conf import settings
-from django.db import migrations, models
-import django.db.models.deletion
-import uuid
-
-
-class Migration(migrations.Migration):
-
-    initial = True
-
-    dependencies = [
-        migrations.swappable_dependency(settings.AUTH_USER_MODEL),
-    ]
-
-    operations = [
-        migrations.CreateModel(
-            name='Profile',
-            fields=[
-                ('name', models.CharField(blank=True, max_length=200, null=True)),
-                ('email', models.EmailField(blank=True, max_length=500, null=True)),
-                ('short_intro', models.CharField(blank=True, max_length=200, null=True)),
-                ('bio', models.TextField(blank=True, null=True)),
-                ('profile_image', models.ImageField(blank=True, default='prfiles/user-default.png', null=True, upload_to='profiles/')),
-                ('social_github', models.CharField(blank=True, max_length=200, null=True)),
-                ('social_twitter', models.CharField(blank=True, max_length=200, null=True)),
-                ('social_linkedin', models.CharField(blank=True, max_length=200, null=True)),
-                ('social_website', models.CharField(blank=True, max_length=200, null=True)),
-                ('created', models.DateTimeField(auto_now_add=True)),
-                ('id', models.UUIDField(default=uuid.uuid4, editable=False, primary_key=True, serialize=False, unique=True)),
-                ('user', models.OneToOneField(blank=True, null=True, on_delete=django.db.models.deletion.CASCADE, to=settings.AUTH_USER_MODEL)),
-            ],
-        ),
-    ]

### 2023-03-20 django/CS476P/CS476P/users/migrations/0002_profile_username.py

@@ -1,18 +1,0 @@
-# Generated by Django 4.1.7 on 2023-03-02 02:45
-
-from django.db import migrations, models
-
-
-class Migration(migrations.Migration):
-
-    dependencies = [
-        ('users', '0001_initial'),
-    ]
-
-    operations = [
-        migrations.AddField(
-            model_name='profile',
-            name='username',
-            field=models.CharField(blank=True, max_length=200, null=True),
-        ),
-    ]

### 2023-03-20 django/CS476P/CS476P/users/migrations/0003_profile_location_skill.py

@@ -1,30 +1,0 @@
-# Generated by Django 4.1.7 on 2023-03-02 06:01
-
-from django.db import migrations, models
-import django.db.models.deletion
-import uuid
-
-
-class Migration(migrations.Migration):
-
-    dependencies = [
-        ('users', '0002_profile_username'),
-    ]
-
-    operations = [
-        migrations.AddField(
-            model_name='profile',
-            name='location',
-            field=models.CharField(blank=True, max_length=200, null=True),
-        ),
-        migrations.CreateModel(
-            name='Skill',
-            fields=[
-                ('name', models.CharField(blank=True, max_length=200, null=True)),
-                ('description', models.TextField(blank=True, null=True)),
-                ('created', models.DateTimeField(auto_now_add=True)),
-                ('id', models.UUIDField(default=uuid.uuid4, editable=False, primary_key=True, serialize=False, unique=True)),
-                ('owner', models.ForeignKey(blank=True, null=True, on_delete=django.db.models.deletion.CASCADE, to='users.profile')),
-            ],
-        ),
-    ]

### 2023-03-20 django/CS476P/CS476P/users/models.py

@@ -1,66 +1,0 @@
-from django.db import models
-from django.contrib.auth.models import User
-import uuid
-
-# Create your models here.
-
-class Profile(models.Model):
-    user = models.OneToOneField(User, on_delete=models.CASCADE,null=True,blank=True)
-    name = models.CharField(max_length=200,blank=True,null=True)
-    email = models.EmailField(max_length=500,blank=True,null=True)
-    username = models.CharField(max_length=200,blank=True,null=True)
-    location = models.CharField(max_length=200,blank=True,null=True)
-    short_intro = models.CharField(max_length=200,blank=True,null=True)
-    bio = models.TextField(blank=True,null=True)
-    profile_image = models.ImageField(null=True,blank=True,upload_to='profiles/', default="prfiles/user-default.png")
-    social_github = models.CharField(max_length=200,blank=True,null=True)
-    social_twitter = models.CharField(max_length=200,blank=True,null=True)
-    social_linkedin = models.CharField(max_length=200,blank=True,null=True)
-    social_website = models.CharField(max_length=200,blank=True,null=True)
-    created = models.DateTimeField(auto_now_add=True)
-    id = models.UUIDField(default=uuid.uuid4,unique=True,primary_key=True,editable=False)
-
-    def __str__(self):
-        return str(self.user.username)
-    
-class Skill(models.Model):
-    owner = models.ForeignKey(Profile, on_delete=models.CASCADE, null=True, blank=True)
-    name = models.CharField(max_length=200,blank=True,null=True)
-    description = models.TextField(null=True,blank=True)
-    created = models.DateTimeField(auto_now_add=True)
-    id = models.UUIDField(default=uuid.uuid4, unique = True,primary_key=True,editable=False)
-
-    def __str__(self):
-        return str(self.name)
-    
-    
-    
-    
-    
-    class Test(models.Model):
-    name = models.CharField(max_length=200,blank=True,null=True)
-    description = models.TextField(null=True,blank=True)
-    created = models.DateTimeField(auto_now_add=True)
-    id = models.UUIDField(default=uuid.uuid4, unique = True,primary_key=True,editable=False)
-    def __str__(self):
-        return str(self.name)
-    
-
-
-
-
-
-
-
-class Forms(models.Model):
-    form_id = models.AutoField(primary_key=True)
-    user_id = models.IntegerField(blank=True, null=True) #models.ForeignKey('Users', models.DO_NOTHING, blank=True, null=True)
[…]

### 2023-03-20 django/CS476P/CS476P/users/urls.py

@@ -1,18 +1,0 @@
-from django.urls import path
-from . import views
-
-urlpatterns = [
-    path('login/', views.loginUser, name="login"),
-    path('logout/', views.logoutUser, name="logout"),
-    path('register/', views.registerUser, name="register"),
-
-    path('profiles', views.profiles, name="profiles"),
-    path('profiles/<str:pk>/', views.userProfile, name="user-profile"),
-
-    path('account/', views.userAccount, name="account"),   
-    path('test/', views.tests, name="test123"),
-    #path('createsurvey/', views.saveFormEditor, name='form'),
-    path('formEditor/', views.formEditor, name="formEditor"),
-    #path('createsurvey/', views.saveFormEditor, name="saveFormEditor"),
-    path('saveformeditor/', views.saveFormEditor, name="saveFormEditor"),
-]

### 2023-03-20 django/CS476P/CS476P/users/views.py

@@ -1,133 +1,0 @@
-from django.shortcuts import render, redirect
-from django.contrib.auth import login, authenticate, logout
-from django.contrib.auth.models import User
-from django.urls import path
-from .models import Profile
-from django.contrib.auth.decorators import login_required
-from django.contrib import messages
-from .forms import CustomUserCreationForm
-
-import json
-from django.http import JsonResponse
-from .models import Forms
-from django.contrib import messages
-
-
-
-# Create your views here.
-
-def loginUser(request):
-    page = 'login'
-    if request.user.is_authenticated:
-        return redirect('profiles')
-    
-
-    if request.method =='POST':
-        username = request.POST['username']
-        password = request.POST['password']
-
-        try:
-            user = User.objects.get(username=username)
-        except:
-            messages.error(request, 'Username does not exist')
-
-        user = authenticate(request, username=username, password=password)
-
-        if user is not None:
-            login(request, user)
-            return redirect('profiles')
-        else:
-            messages.error(request, 'Username or password is incorrect')
-
-    return render(request, 'users/login_register.html') #########
-    
-def logoutUser(request):
-    logout(request)
-    messages.error(request, 'User was logged out')
-    return redirect('login')
-
-def registerUser(request):
-    page = 'register'
-    form = CustomUserCreationForm()
-
-    if request.method == 'POST':
-        form = CustomUserCreationForm(request.POST)
-        if form.is_valid():
-            user = form.save(commit=False)
-            user.username = user.username.lower()
-            user.save()
-
-            messages.success(request, 'User account was created!')
-
-            login(request, user)
-            return redirect('profiles')
-        
-        else:
-            messages.error(request, 'An error has occurred!')
-
-
-    context = {'page':page, 'form':form}
-    return render(request, 'users/login_register.html', context)
-
-
-def profiles(request):
-    profiles = Profile.objects.all()
-    context = {'profiles':profiles}
-    return render(request, 'users/profiles.html', context)
-
-def userProfile(request, pk):
-    profile = Profile.objects.get(id=pk)
-    context = {'profile':profile}
-    return render(request, 'users/user-profile.html', context)
-
-@login_required(login_url='login')
-def userAccount(request):
-    profile = request.user.profile
-    context = {'profile':profile}
-    return render(request, 'users/account.html', context)
-
-
-def tests(request):
-    tests = Test.objects.all()
-    context = {'tests':tests}
[…]

### 2023-03-20 django/dLocal/dLocal/projects/urls.py

@@ -3,7 +3,7 @@ from . import views
 
 urlpatterns = [
     path('', views.home, name="home"),
-    path('createsurvey/', views.createsurvey, name="createsurvey"),
+
     path('landingpage/', views.landingpage, name="landingpage"),
     
     path('survey/', views.survey, name="survey"),

### 2023-03-20 django/dLocal/dLocal/users/admin.py

@@ -2,7 +2,6 @@ from django.contrib import admin
 
 # Register your models here.
 
-from .models import Profile, Skill
+from .models import Profile
 
 admin.site.register(Profile)
-admin.site.register(Skill)

### 2023-03-20 django/dLocal/dLocal/users/models.py

@@ -2,7 +2,6 @@ from django.db import models
 from django.contrib.auth.models import User
 import uuid
 
-# Create your models here.
 
 class Profile(models.Model):
     user = models.OneToOneField(User, on_delete=models.CASCADE,null=True,blank=True)
@@ -22,28 +21,3 @@ class Profile(models.Model):
 
     def __str__(self):
         return str(self.user.username)
-    
-class Skill(models.Model):
-    owner = models.ForeignKey(Profile, on_delete=models.CASCADE, null=True, blank=True)
-    name = models.CharField(max_length=200,blank=True,null=True)
-    description = models.TextField(null=True,blank=True)
-    created = models.DateTimeField(auto_now_add=True)
-    id = models.UUIDField(default=uuid.uuid4, unique = True,primary_key=True,editable=False)
-
-    def __str__(self):
-        return str(self.name)
-    
-    
-class Forms(models.Model):
-    form_id = models.AutoField(primary_key=True)
-    user_id = models.IntegerField(blank=True, null=True) #models.ForeignKey('Users', models.DO_NOTHING, blank=True, null=True)
-    title = models.CharField(max_length=255, blank=True, null=True)
-    description = models.CharField(max_length=255, blank=True, null=True)
-    created_at = models.DateTimeField(blank=True, null=True)
-    updated_at = models.DateTimeField(blank=True, null=True)
-    is_active = models.IntegerField(blank=True, null=True)
-    form_json = models.TextField(db_column='form_JSON', blank=True, null=True)  # Field name made lowercase.
-
-    class Meta:
-        managed = False
-        db_table = 'forms'

### 2023-03-20 django/dLocal/dLocal/users/urls.py

@@ -5,10 +5,5 @@ urlpatterns = [
     path('login/', views.loginUser, name="login"),
     path('logout/', views.logoutUser, name="logout"),
     path('register/', views.registerUser, name="register"),
-
-    path('profiles', views.profiles, name="profiles"),
-    path('profiles/<str:pk>/', views.userProfile, name="user-profile"),
-
-    path('account/', views.userAccount, name="account"),   
-    # path('formEditor/', views.formEditor, name="formEditor"),   
+    path('profiles', views.profiles, name="profiles"),  
 ]

### 2023-03-20 django/dLocal/dLocal/users/views.py

@@ -90,8 +90,8 @@ def user_forms(request, idd):
         
         # passing the user_id, user_forms, form_ids, and form_titles to the profiles.html template
         return render(request, 'users/profiles.html',  {'id': user_id, 'forms': forms})
-
-
+    
+    
 def profiles(request):
     if not (request.user.is_authenticated):
         return redirect('login')
@@ -103,15 +103,3 @@ def profiles(request):
         return user_forms(request, user_id)
     
     return render(request, 'users/profiles.html', context)
-
-def userProfile(request, pk):
-    profile = Profile.objects.get(id=pk)
-    context = {'profile':profile}
-    return render(request, 'users/user-profile.html', context)
-
-@login_required(login_url='login')
-def userAccount(request):
-    profile = request.user.profile
-    context = {'profile':profile}
-    return render(request, 'users/account.html', context)
-

### 2023-03-20 django/dLocal/dOLD/dLocal/asgi.py

@@ -1,16 +1,0 @@
-"""
-ASGI config for dLocal project.
-
-It exposes the ASGI callable as a module-level variable named ``application``.
-
-For more information on this file, see
-https://docs.djangoproject.com/en/4.1/howto/deployment/asgi/
-"""
-
-import os
-
-from django.core.asgi import get_asgi_application
-
-os.environ.setdefault("DJANGO_SETTINGS_MODULE", "dLocal.settings")
-
-application = get_asgi_application()

### 2023-03-20 django/dLocal/dOLD/dLocal/settings.py

@@ -1,123 +1,0 @@
-"""
-Django settings for dLocal project.
-
-Generated by 'django-admin startproject' using Django 4.1.7.
-
-For more information on this file, see
-https://docs.djangoproject.com/en/4.1/topics/settings/
-
-For the full list of settings and their values, see
-https://docs.djangoproject.com/en/4.1/ref/settings/
-"""
-
-from pathlib import Path
-
-# Build paths inside the project like this: BASE_DIR / 'subdir'.
-BASE_DIR = Path(__file__).resolve().parent.parent
-
-
-# Quick-start development settings - unsuitable for production
-# See https://docs.djangoproject.com/en/4.1/howto/deployment/checklist/
-
-# SECURITY WARNING: keep the secret key used in production secret!
-SECRET_KEY = "django-insecure-h^c+d@5&26s8b)*6cajr3cfabsermi&rz02jfc@#w06a4lsevj"
-
-# SECURITY WARNING: don't run with debug turned on in production!
-DEBUG = True
-
-ALLOWED_HOSTS = []
-
-
-# Application definition
-
-INSTALLED_APPS = [
-    "django.contrib.admin",
-    "django.contrib.auth",
-    "django.contrib.contenttypes",
-    "django.contrib.sessions",
-    "django.contrib.messages",
-    "django.contrib.staticfiles",
-]
-
-MIDDLEWARE = [
-    "django.middleware.security.SecurityMiddleware",
-    "django.contrib.sessions.middleware.SessionMiddleware",
-    "django.middleware.common.CommonMiddleware",
-    "django.middleware.csrf.CsrfViewMiddleware",
-    "django.contrib.auth.middleware.AuthenticationMiddleware",
-    "django.contrib.messages.middleware.MessageMiddleware",
-    "django.middleware.clickjacking.XFrameOptionsMiddleware",
-]
-
-ROOT_URLCONF = "dLocal.urls"
-
-TEMPLATES = [
-    {
-        "BACKEND": "django.template.backends.django.DjangoTemplates",
-        "DIRS": [],
-        "APP_DIRS": True,
-        "OPTIONS": {
-            "context_processors": [
-                "django.template.context_processors.debug",
-                "django.template.context_processors.request",
-                "django.contrib.auth.context_processors.auth",
-                "django.contrib.messages.context_processors.messages",
-            ],
[…]

### 2023-03-20 django/dLocal/dOLD/dLocal/urls.py

@@ -1,21 +1,0 @@
-"""dLocal URL Configuration
-
-The `urlpatterns` list routes URLs to views. For more information please see:
-    https://docs.djangoproject.com/en/4.1/topics/http/urls/
-Examples:
-Function views
-    1. Add an import:  from my_app import views
-    2. Add a URL to urlpatterns:  path('', views.home, name='home')
-Class-based views
-    1. Add an import:  from other_app.views import Home
-    2. Add a URL to urlpatterns:  path('', Home.as_view(), name='home')
-Including another URLconf
-    1. Import the include() function: from django.urls import include, path
-    2. Add a URL to urlpatterns:  path('blog/', include('blog.urls'))
-"""
-from django.contrib import admin
-from django.urls import path
-
-urlpatterns = [
-    path("admin/", admin.site.urls),
-]

### 2023-03-20 django/dLocal/dOLD/dLocal/wsgi.py

@@ -1,16 +1,0 @@
-"""
-WSGI config for dLocal project.
-
-It exposes the WSGI callable as a module-level variable named ``application``.
-
-For more information on this file, see
-https://docs.djangoproject.com/en/4.1/howto/deployment/wsgi/
-"""
-
-import os
-
-from django.core.wsgi import get_wsgi_application
-
-os.environ.setdefault("DJANGO_SETTINGS_MODULE", "dLocal.settings")
-
-application = get_wsgi_application()

### 2023-03-20 django/dLocal/dOLD/manage.py

@@ -1,22 +1,0 @@
-#!/usr/bin/env python
-"""Django's command-line utility for administrative tasks."""
-import os
-import sys
-
-
-def main():
-    """Run administrative tasks."""
-    os.environ.setdefault("DJANGO_SETTINGS_MODULE", "dLocal.settings")
-    try:
-        from django.core.management import execute_from_command_line
-    except ImportError as exc:
-        raise ImportError(
-            "Couldn't import Django. Are you sure it's installed and "
-            "available on your PYTHONPATH environment variable? Did you "
-            "forget to activate a virtual environment?"
-        ) from exc
-    execute_from_command_line(sys.argv)
-
-
-if __name__ == "__main__":
-    main()

### 2023-03-20 paper/main.tex

--- 2023-03-15 paper/main.tex
@@
 \subsection{For each user role, provide the use case diagram with all the use cases and actors.}
+
 \hfill \break
-
+\begin{figure}[h]
+\centering
 \includegraphics[width=0.70\textwidth]{caseDiagram.png}
+\caption{Use Case Diagrams for both the Feedback Gatherer and Respondent}
+\end{figure}
 
@@
 \begin{enumerate}
-    \item The feedback gatherer can create a survey after registering.
-The feedback gatherer has the option to delete an existing survey or view statistics and responses to an existing survey.
-After creating a survey, the feedback gatherer can view the QR code to administer the created survey.
+    \item The main use case for the feedback gatherer includes: 
+    \begin{enumerate}
+        \item Creating a survey after registering
+        \item Viewing statistics and responses to an existing survey
+        \item Viewing the QR code for the survey they created
+    \end{enumerate}
     \hfill \break
 
-    \includegraphics[width=0.70\textwidth]{feedbackGatherer.png}
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=0.65\textwidth]{feedbackGatherer.png}
+        \caption{Feedback Gatherer Activity Diagram}
+    \end{figure}
 \newpage
-    \item The respondent can scan the QR code to take a survey created by a feedback gatherer. The respondent enters responses to the survey and submit the responses.
+    \item The main use case for the respondent includes:
+    \begin{enumerate}
+        \item Scanning the QR code to access the survey previously created by the feedback gatherer
+        \item Enter responses to the given survey questions
+        \item Submit the completed survey
+    \end{enumerate}
     \linebreak
     \hfill \break
+    \begin{figure}[h]
+    \centering
     \includegraphics[width=0.70\textwidth]{respondent.png}
+    \caption{Respondent Activity Diagram}
+    \end{figure}
 
@@
 \linebreak
-    \hfill \break
+
 \textbf{Correctness:}
@@
     \begin{itemize}
-        \item A survey correctly displays the questions and answer choices entered by the feedback gatherer during creation. 
+        \item A survey correctly displays the questions and answer choices entered by the feedback gatherer during survey creation. 
         \item Accurate statistics for a survey are shown to the feedback gatherer.
@@
         \item  When a feedback gatherer creates the survey, the QR code for the survey is created in a timely manner.
-        \item When responses to a survey are submitted, they are available for view by the feedback gatherer in a timely manner.
+        \item When responses to a survey are submitted, they are available to be viewed by the feedback gatherer in a timely manner.
     \end{itemize}
@@
     \begin{itemize}
-        \item A respondent is taken to the survey in a timely manner after scanning a QR code for a survey.
-        \item A respondent is given a confirmation in a timely manner after submitting a survey.
+        \item The respondent is taken to the survey in a timely manner after scanning the QR code for a survey.
+        \item The respondent is given the submission confirmation in a timely manner after submitting a survey.
     \end{itemize}
@@
     \begin{itemize}
-        \item  If a feedback gatherer attempts to submit a blank survey, submission is denied with a warning.
-        \item If a feedback gatherer forgets to select a type of answer to a question, submission is denied with a warning.
+        \item  If a feedback gatherer attempts to submit a blank survey, the submission is denied with a warning.
+        \item If a feedback gatherer forgets to select a type of answer for a question, submission is denied with a warning.
     \end{itemize}
@@
     \begin{itemize}
-        \item If a respondent attempts to submit a survey with one or more unanswered questions, submission is denied and unanswered questions are marked.
+        \item If a respondent attempts to submit a survey with one or more unanswered questions, the submission is denied and unanswered questions are marked as such.
         \item If a respondent attempts to exit the survey after answering one or more questions, a warning is shown.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage 
+\section{Top-level and Low-level Software Design}
+\subsection{Provide the MVC architecture according to the selected Web framework. Also, describe at least three benefits of MVC for your application.}
+\newline
+\hfill
 
-\section{Top-level and Low-level Software Design}
-\subsection{Provide the MVC architecture according to the selected Web frame- work. Also, describe at least three benefits of MVC for your application.}
-\linebreak
-    \hfill \break
+Django uses MVT (Model View Template) architecture which is a variation of the traditional MVC (Model View Controller) architecture.
+Similar to the MVC, the model in MVT represents the data and business logic.
+The view in MVT is split into two parts: the template displays the data, and the view handles the user input and interacts with the model to retrieve and manipulate the data.
+Similarly to the MVC, MVT separates layers and keeps the code organized and maintainable, while also simplifying the view by separating it into two parts.
+\newline
+
+The MVT architecture allows the developer to work on each layer in parallel and then integrate them efficiently.
+In our project, we used this feature to build and test the three main functions: user authentication process, creation of surveys by the feedback gatherers, and submission of surveys by the respondents.
+We were able to implement one functionality at a time while working on all of the layers in parallel.
+One member created the HTML templates while another worked on the models to store the data.
+Views were then set up followed by finalizing the templates to display the data.
+Using this method, we were able to develop our web application much faster.
+\newline
+
+The MVT architecture allows the developers to make modifications that will not affect the entire model.
+During development, many changes were required on the templates to enhance the user interface.
+It was beneficial that the changes in the HTML and CSS only affected the templates and not the entirety of the web application.
+Many adjustments were also made in the views as well including setting page restrictions for authentication and changing the interactions on the models for submitting data using the forms.
+Again, the MVT architecture made this process simpler by isolating the modifications.
+\newline
+\newpage
+One major advantage of the Django MVT architecture is the simplified testing process.
+Since all layers of the application are structurally defined, we were able to test our three main functionalities as we were developing them.
+For example, for the creation of surveys, the clearly defined structure of the template, model, and view helped us to run tests efficiently.
+Using an account, we created survey and submitted them and checked the database to verify that the data from the surveys was accurately stored.
+The clear structure also allowed for efficient debugging and modifications because we knew which template, model, and view were responsible for which functionality.
+\newline
+
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.80\textwidth]{mvt.png}
+        \caption{MVT Architecture}
+    \end{figure}
+
+    \newpage
 
@@
 For each class, provide the data types of the attributes and prototypes of the methods.}
+
+\textbf{Observer Patterns}
+
+Similar to the MVC architecture, the views in Django’s MVT architecture are the dependent objects while the models are the independent objects.
+In our application, the observer pattern can be used to manage the relationship between the views and the models by notifying the different views whenever there are changes in the model’s data.
+This can be useful since there are multiple views that are affected by the changes in the data.
+For example, when a user adds or deletes a survey, this change would be reflected in the survey model.
+All of the views related to this model would be notified of these changes.
+The user profile template would display the addition or the deletion of a survey while a new survey page template would be created or deleted.
+The observer model can be useful in maintaining consistency between the related objects and keeping them up to date.
+\newline
+\hfill \break
+\textbf{Factory Patterns}
+
+In our application, the factory design pattern can be used to store the family of objects in one class and to keep the code of building the objects hidden from the clients.
+For example, a factory class can be used for the creation of surveys, which is a family of related objects.
+The factory class would be the centralized class that creates a family of different surveys.
+This results in consistent products for all clients while having a highly maintainable program with no duplication of code.
+The factory class would return a survey depending on the questions and the type of answers selected by the client.
+The factory design pattern is useful for our application because we have many users that need the same family of objects which is the survey.
+
 \linebreak
@@
 
+\newpage
 \subsection{Provide the class diagram of the whole system by incorporating the two design patterns.}
@@
     \hfill \break
+\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \linebreak
-    \hfill \break
 \url{https://github.com/zachary-huber/feedback-app}
@@
 \linebreak
-    \hfill \break
-\url{https://www.viewnote.app/}
+\url{https://commentcorner.ngrok.app/}
 \hfill \break
 
+\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
    \item CSS
-   \item PHP
+   \item SQL
+   \item Python
 \end{enumerate}
+\hfill
+\newline
 
@@
 \begin{enumerate}
-   \item thing
-   \begin{description}
-     \item description
-   \end{description}
-   \item thing
+   \item  Django web and database frameworks - \url{https://docs.djangoproject.com/en/4.1/}
+   \begin{itemize}
+     \item User Authentication - built in
+     \begin{itemize}
+         \item Login
+         \item Logout
+         \item Register
+     \end{itemize}
+   \end{itemize}
+   \item QR code - \url{https://api.qrserver.com/v1/create-qr-code/?data=data}
+    \item Form Generation - made by scratch
+    \item Survey Generation - made by scratch
 \end{enumerate}
+\newpage
 
@@
 \begin{enumerate}
-   \item React
+   \item Django
    \begin{description}
-     \item description
+     \item The main functionality of our web application requires a web framework with a database that can be used to store and load a user’s data such as their surveys and responses.
+Django allows quick and efficient development of our web application by providing the framework and the modules needed.
+The nuisance of creating and connecting to a database is already implemented in Django, so we were able to quickly test the storage and loading of our data in the early stages of development.
+Migration of our data was also made simple by Django because it only requires running a few commands in the terminal.
    \end{description}
-   \item Django
+   \item[]
+   \item ngrok
+    \begin{description}
+        Ngrok provides web application hosting services with a publicly accessible URL.
+It is a free tool which allows secure tunneling from a public URL to our local application.
+This feature of ngrok allowed us to test the display of data on the templates after the extraction and loading of data from the model layer directly on the public URL.
+It was helpful for all of the members to view the updates in real time on the public URL.
+    \end{description}
+    \item[]
+   \item MySQL
+   \begin{description}
+       The data in the model layer of Django was migrated to the MySQL database.
+The MySQL database was used to store our user data because it is a reliable, free, and open-source database.
+Being the most popular database, it is a secure and scalable with the ability for complete customization.
+Any changes made to our model could be handled by the MySQL database.
+Also, the assurance of continuous uptime allowed us to consistently work on our application.
+   \end{description}
 \end{enumerate}
-
+\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Correctness testing using four test cases (screenshots of both inputs and outputs).}
+\newline
+
+\textbf{Feedback gatherer:}
+\begin{itemize}
+    \item[] Input: Feedback gatherer creates a survey by selecting the types of answers and entering the questions.
+
+Output: When they click the “Create Survey” button, a QR code is generated.
+
+Input: Feedback gatherer clicks on one of the past surveys.
+
+Output: Feedback gatherer can view the responses to the correct survey.
+\end{itemize}
+
+\hfill \break
+\textbf{Respondent:}
+\begin{itemize}
+    \item[] Input: Respondent scans the QR code.
+    \item[] Output: Respondent is taken to the correct survey.
+    \item[] Input: Respondent completes the survey and clicks submit.
+    \item[] Output: Respondent is taken to the thank you page.
+\end{itemize}
+
+\newpage
+
 \subsection{Robustness testing using four test cases (screenshots of both inputs and outputs).}
+\newline
+
+\textbf{Feedback gatherer:}
+
+\begin{itemize}
+    \item[] Input: Feedback gatherer tries to go to the sign up page while already logged in.
+
+Output: Feedback gatherer is redirected to landing page.
+
+Input: Feedback gatherer tries to go to the login page while already logged in.
+
+Output: Feedback gatherer is redirected to landing page.
+\end{itemize}
+\newline 
+\hfill \break
+
+\textbf{Respondent:}
+\begin{itemize}
+    \item[] Input: Respondent tries to go the landing page while not logged in.
+
+Output: Respondent is redirected to login page.
+
+Input: Respondent tries to go the create survey page while not logged in.
+
+Output: Respondent is redirected to login page.
+
+\end{itemize}
+\newpage
+
 \subsection{Time-eﬀiciency testing of two functions (with screenshots). Indicate the method you used to measure the time.}
+\newline
+
+\textbf{Feedback gatherer:}
+\begin{itemize}
+    \item[] Create survey: Time taken for the survey data to be stored in the database and the QR code to be generated.
+
+View responses: Time taken for the response data to be shown to the feedback gatherer after clicking a past survey.
+\end{itemize}
+\newline
+\hfill \break
+
+\textbf{Respondent:}
+\begin{itemize}
+    \item[] Go to survey: Time taken for the survey to be loaded from the database when the QR code is scanned.
+
+Submit responses: Time taken for the response data to be stored in the database and to show the respondent that the responses were successfully submitted.
+
+\end{itemize}
+\newline
+\hfill \break
+Method: Use inspect network in Google Chrome.
 

### 2023-03-20 django/dLocal/dLocal/projects/admin.py
updated form/survey UI

@@ -2,13 +2,9 @@ from django.contrib import admin
 
 # Register your models here.
 
-from .models import Project, Review, Tag, Form, Response
+from .models import Project, Tag, Form, Response
 
 admin.site.register(Project)
-admin.site.register(Review)
 admin.site.register(Tag)
-
-
-
 admin.site.register(Form)
 admin.site.register(Response)

### 2023-03-20 django/dLocal/dLocal/projects/migrations/0007_merge_20230319_1823.py

@@ -1,0 +1,13 @@
+# Generated by Django 4.1.7 on 2023-03-20 00:23
+
+from django.db import migrations
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ("projects", "0006_forms_projectsform"),
+        ("projects", "0006_rename_created_response_created_at_and_more"),
+    ]
+
+    operations = []

### 2023-03-20 django/dLocal/dLocal/projects/models.py

@@ -21,21 +21,7 @@ class Project(models.Model):
     def __str__(self):
         return self.title
 
-class Review(models.Model):
-    VOTE_TYPE = (
-        ('up', 'Up Vote'),
-        ('down', 'Down Vote'),
-    )
-    #owner =
-    project = models.ForeignKey(Project, on_delete=models.CASCADE)
-    body = models.TextField(null=True,blank=True)
-    value = models.CharField(max_length=200, choices = VOTE_TYPE)
-    created = models.DateTimeField(auto_now_add=True)
-    id = models.UUIDField(default=uuid.uuid4,unique=True,primary_key=True,editable=False)
 
-    def __str__(self):
-        return self.value
-    
 class Tag(models.Model):
     name = models.CharField(max_length=200)
     created = models.DateTimeField(auto_now_add=True)
@@ -44,9 +30,6 @@ class Tag(models.Model):
     def __str__(self):
         return self.name
     
-
-
-
 
 class Form(models.Model):
     id = models.UUIDField(default=uuid.uuid4,unique=True,primary_key=True,editable=False)

### 2023-03-20 django/dLocal/dLocal/static/js/survey.js

@@ -219,6 +219,10 @@ function addResponseElement(inputType, questionHeading){
             newLabel.setAttribute("for", "true");
             newLabel.innerHTML = "True";
             newDiv.appendChild(newLabel);
+
+            var br = document.createElement("br")
+            newDiv.appendChild(br);
+
             var newInput = createInputElement("radio");
             newInput.setAttribute("name", "true-false" + responseInputs);
             newInput.setAttribute("value", "false");
@@ -236,23 +240,31 @@ function addResponseElement(inputType, questionHeading){
             newDiv.appendChild(newInput);
             var newLabel = document.createElement("label");
             newLabel.setAttribute("for", "Disagree");
-            newLabel.innerHTML = "1 = Disagree";
+            newLabel.innerHTML = "Disagree";
             newDiv.appendChild(newLabel);
+
+            var br = document.createElement("br")
+            newDiv.appendChild(br);
+
             var newInput = createInputElement("radio");
             newInput.setAttribute("name", "attitude-scale" + responseInputs);
             newInput.setAttribute("value", "Neutral");
             newDiv.appendChild(newInput);
             var newLabel = document.createElement("label");
             newLabel.setAttribute("for", "Neutral");
-            newLabel.innerHTML = "2 = Neutral";
+            newLabel.innerHTML = "Neutral";
             newDiv.appendChild(newLabel);
+
+            var br = document.createElement("br");
+            newDiv.appendChild(br);
+
             var newInput = createInputElement("radio");
             newInput.setAttribute("name", "attitude-scale" + responseInputs);
             newInput.setAttribute("value", "Agree");
             newDiv.appendChild(newInput);
             var newLabel = document.createElement("label");
             newLabel.setAttribute("for", "Agree");
-            newLabel.innerHTML = "3 = Agree";
+            newLabel.innerHTML = "Agree";
             newDiv.appendChild(newLabel);
             break;
             default:

### 2023-03-20 django/dLocal/dLocal/users/models.py

@@ -8,14 +8,6 @@ class Profile(models.Model):
     name = models.CharField(max_length=200,blank=True,null=True)
     email = models.EmailField(max_length=500,blank=True,null=True)
     username = models.CharField(max_length=200,blank=True,null=True)
-    location = models.CharField(max_length=200,blank=True,null=True)
-    short_intro = models.CharField(max_length=200,blank=True,null=True)
-    bio = models.TextField(blank=True,null=True)
-    profile_image = models.ImageField(null=True,blank=True,upload_to='profiles/', default="prfiles/user-default.png")
-    social_github = models.CharField(max_length=200,blank=True,null=True)
-    social_twitter = models.CharField(max_length=200,blank=True,null=True)
-    social_linkedin = models.CharField(max_length=200,blank=True,null=True)
-    social_website = models.CharField(max_length=200,blank=True,null=True)
     created = models.DateTimeField(auto_now_add=True)
     id = models.UUIDField(default=uuid.uuid4,unique=True,primary_key=True,editable=False)
 

### 2023-03-20 amplify/backend/types/amplify-dependent-resources-ref.d.ts
removed amplify files

@@ -1,20 +1,0 @@
-export type AmplifyDependentResourcesAttributes = {
-  "api": {
-    "feedbackapp": {
-      "GraphQLAPIEndpointOutput": "string",
-      "GraphQLAPIIdOutput": "string",
-      "GraphQLAPIKeyOutput": "string"
-    }
-  },
-  "auth": {
-    "feedbackapp5a30c472": {
-      "AppClientID": "string",
-      "AppClientIDWeb": "string",
-      "IdentityPoolId": "string",
-      "IdentityPoolName": "string",
-      "UserPoolArn": "string",
-      "UserPoolId": "string",
-      "UserPoolName": "string"
-    }
-  }
-}

### 2023-03-20 paper/main.tex
updates to paper

@@
 \usepackage{wrapfig}
+\usepackage{multicol}
+
+\usepackage{listings}
+\usepackage{color}
+
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+
+\lstset{frame=tb,
+  language=Java,
+  aboveskip=0mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  breaklines=true,
+  breakatwhitespace=true,
+  tabsize=3
+}
 
@@
     \end{enumerate}
-    \hfill \break
 
@@
         \centering
-        \includegraphics[width=0.65\textwidth]{feedbackGatherer.png}
+        \includegraphics[width=0.55\textwidth]{feedbackGatherer2.png}
         \caption{Feedback Gatherer Activity Diagram}
@@
     \linebreak
-    \hfill \break
+
     \begin{figure}[h]
     \centering
-    \includegraphics[width=0.70\textwidth]{respondent.png}
+    \includegraphics[width=0.70\textwidth]{respondent2.png}
     \caption{Respondent Activity Diagram}
@@
 \newline
-\hfill \break
+\clearpage
+
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.75\textwidth]{AuthUserClass.png}
+        \caption{AuthUser Class}
+\end{figure}
+
+\begin{lstlisting}
+AuthUser Data Algorithm
+
+interface class Subject
+{
+	protected observerList: array of Observer
+	public void register(Observer)
+	public void unregister(Observer)
+	public void notify()
+}
+class AuthUser Data implements Subject
+{
+	private int is_superuser, is_staff, is_active
+	private string password, last_login, username, first_name, last_name, email, date_joined
+	public void register(Observer obs)
+		observerList.add(obs)
+	public void unregister(Observer obs)
+		observerList.delete(obs)
+	public void notify()
+		for each obs in observerList
+			obs.update(is_superuser, is_staff, is_active, password, last_login, username, first_name, last_name, email, date_joined)
+	public void sendAuthUser() //calls notify()
+	public type getState()
+		return subjectState
+}
+
+interface class Observer
+{
+	public void update(int, int, int, string, string, string, string, string, string, string)
+}
+class authUser implement Observer
+{
+	private int is_superuser, is_staff, is_active
+	private string password, last_login, username, first_name, last_name, email, date_joined
+	public void update(int is_superuserX, int is_staffX, int is_activeX, astring passwordX, string last_loginX, string usernameX, string first_nameX, string last_nameX, string emailX, string date_joinedX)
+	{
+		is_superuser = is_superuserX
+		is_staff = is_staffX
+		is_active = is_activeX
+		password = passwordX
+		last_login = last_loginX
+		username = usernameX
+		first_name = first_nameX
+		last_name = last_nameX
+		email = emailX
+		date_joined = date_joinedX
+		displayView()
+	}
+	public void displayView()
+}
+\end{lstlisting}
+\clearpage
+
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.85\textwidth]{ResponsesData.png}
+        \caption{Responses Data}
+    \end{figure}
+
+\begin{lstlisting}
+Responses Data Algorithm
+
+interface class Subject
+{
+	protected observerList: array of Observer
+	public void register(Observer)
+	public void unregister(Observer)
+	public void notify()
+}
+class ResponsesData implements Subject
+{
+	private int response_id, form_id, user_id
+	private string response_json, created_at, updated_at
+	public void register(Observer obs)
+		observerList.add(obs)
+	public void unregister(Observer obs)
+		observerList.delete(obs)
+	public void notify()
+		for each obs in observerList
+			obs.update(response_id, form_id, user_id, response_json, created_at, updated_at)
+	public void sendResponse() //calls notify()
+	public type getState()
+		return subjectState
+}
+
+interface class Observer
+{
+	public void update(int, int, int, string, string, string)
+}
+class deleteForm implement Observer
+{
+	private int response_id, form_id, user_id
+	private string response_json, created_at, updated_at
+	public void update(int response_idX, int form_idX, int user_idX, string response_jsonX, string created_atX, string updated_atX)
+	{
+		response_id = response_idX
+		form_id = form_idX
+		user_id = user_idX
+		response_json = response_jsonX
+		created_at = created_atX
+		updated_at = updated_atX
+		displayView()
+	}
+	public void displayView()
+}
+class saveResponses implement Observer
+{
+	private int response_id, form_id, user_id
+	private string response_json, created_at, updated_at
+	public void update(int response_idX, int form_idX, int user_idX, string response_jsonX, string created_atX, string updated_atX)
+	{
+		response_id = response_idX
+		form_id = form_idX
+		user_id = user_idX
+		response_json = response_jsonX
+		created_at = created_atX
+		updated_at = updated_atX
+		displayView()
+	}
+	public void displayView()
+}
+class results implement Observer
+{
+	private int response_id, form_id, user_id
+	private string response_json, created_at, updated_at
+	public void update(int response_idX, int form_idX, int user_idX, string response_jsonX, string created_atX, string updated_atX)
+	{
+		response_id = response_idX
+		form_id = form_idX
+		user_id = user_idX
+		response_json = response_jsonX
+		created_at = created_atX
+		updated_at = updated_atX
+		displayView()
+	}
+	public void displayView()
+}
+\end{lstlisting}
+
+\clearpage
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.85\textwidth]{FormsData.png}
+        \caption{Forms Data}
+    \end{figure}
+
+\begin{lstlisting}
+Forms in Projects Application Algorithm
+
+interface class Subject
+{
+	protected observerList: array of Observer
+	public void register(Observer)
+	public void unregister(Observer)
+	public void notify()
+}
+class FormsData implements Subject
+{
+	private int form_id, user_id, is_active
+	private string title, description, created_at, updated_at, form_json
+	public void register(Observer obs)
+		observerList.add(obs)
+	public void unregister(Observer obs)
+		observerList.delete(obs)
+	public void notify()
+		for each obs in observerList
+			obs.update(form_id, user_id, is_active, title, description, created_at, updated_at, form_json)
+	public void sendForms() //calls notify()
+	public type getState()
+		return subjectState
+}
+
+interface class Observer
+{
+	public void update(int, int, int, string, string, string, string, string)	
+}
+class survey implement Observer
+{
+	private int form_id, user_id, is_active
+	private string title, description, created_at, updated_at, form_json
+	public void update(int form_idX, int user_idX, int is_activeX, string titleX, string descriptionX, string created_atX, string updated_atX, string form_jsonX)
+	{
+		form_id = form_idX
+		user_id = user_idX
+		is_active = is_activeX
+		title = titleX
+		description = descriptionX
+		created_at = created_atX
+		updated_at = updated_atX
+		form_json = formjsonX
+		displayView()
+	}
+	public void displayView()
+}
+class saveFormEditor implement Observer
+{
+	private int form_id, user_id, is_active
+	private string title, description, created_at, updated_at, form_json
+	public void update(int form_idX, int user_idX, int is_activeX, string titleX, string descriptionX, string created_atX, string updated_atX, string form_jsonX)
+	{
+		form_id = form_idX
+		user_id = user_idX
+		is_active = is_activeX
+		title = titleX
+		description = descriptionX
+		created_at = created_atX
+		updated_at = updated_atX
+		form_json = formjsonX
+		displayView()
+	}
+	public void displayView()
+}
+class deleteForm implement Observer
+{
+	private int form_id, user_id, is_active
+	private string title, description, created_at, updated_at, form_json
+	public void update(int form_idX, int user_idX, int is_activeX, string titleX, string descriptionX, string created_atX, string updated_atX, string form_jsonX)
+	{
+		form_id = form_idX
+		user_id = user_idX
+		is_active = is_activeX
+		title = titleX
+		description = descriptionX
+		created_at = created_atX
+		updated_at = updated_atX
+		form_json = formjsonX
+		displayView()
+	}
+	public void displayView()
+}
+class results implement Observer
+{
+	private int form_id, user_id, is_active
+	private string title, description, created_at, updated_at, form_json
+	public void update(int form_idX, int user_idX, int is_activeX, string titleX, string descriptionX, string created_atX, string updated_atX, string form_jsonX)
+	{
+		form_id = form_idX
+		user_id = user_idX
+		is_active = is_activeX
+		title = titleX
+		description = descriptionX
+		created_at = created_atX
+		updated_at = updated_atX
+		form_json = formjsonX
+		displayView()
+	}
+	public void displayView()
+}
+\end{lstlisting}
+
+\clearpage
 \textbf{Factory Patterns}
@@
     \hfill \break
+\clearpage
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.75\textwidth]{FactoryAuthUser.png}
+        \caption{AuthUser Class}
+\end{figure}
+
+\begin{lstlisting}
+class AuthUserSimpleFactory
+{
+	public AuthUser createAuthUser(string type)
+	if (type == "AuthUser1") return new AuthUser1()
+	else if (type == "AuthUser2") return new AuthUser2()
+		.
+		.
+		.
+		else if (type == "AuthUserN") return new AuthUserN() 
+}
+class User1
+{
+	private AuthUserSimpleFactory sfo
+	public AuthUser requestAuthUser(string type)
+	{
+		AuthUser myAuthUser = sfo.createAuthUser(type)
+		myAuthUser.register()
+		return myAuthUser
+	{	
+}
+.
+.
+.
+class UserN
+{
+	private AuthUserSimpleFactory sfo
+	public AuthUser requestAuthUser(string type)
+	{
+		AuthUser myAuthUser = sfo.createAuthUser(type)
+		myAuthUser.register()
+		return myAuthUser
+	{	
+}
+abstract class AuthUser
+{
+	protected password, last_login, username, first_name, last_name, email, date_joined: string
+	protected is_superuser, is_staff, is_active: int
+	public void register()	
+	{ }
+}
+class AuthUser1 extends AuthUser
+{
+	AuthUser1() //assign values entered by the user during registration
+	{
+		password = "password1"
+		last_login = "last_login1"
+		username = "username1"
+		first_name = "first_name1"
+		last_name = "last_name1"
+		email = "email1"
+		date_joined = "date_joined1"
+		is_superuser = 0
+		is_staff = 0
+		is_active = 1
+	}
+	public void register()
+	{ }
+}
+.
+.
+.
+class AuthUserN extends AuthUser
+{
+	AuthUserN() //assign user entered values during registration
+	{
+		password = "passwordN"
+		last_login = "last_loginN"
+		username = "usernameN"
+		first_name = "first_nameN"
+		last_name = "last_nameN"
+		email = "emailN"
+		date_joined = "date_joinedN"
+		is_superuser = 0
+		is_staff = 0
+		is_active = 1
+	}
+	public void register()
+	{ }
+}
+\end{lstlisting}
+
+\clearpage
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.8\textwidth]{FactoryForms.png}
+        \caption{Forms Class}
+\end{figure}
+
+\begin{lstlisting}
+class FormsSimpleFactory
+{
+	public forms createForms(string type)
+	if (type == "Forms1") return new Forms1()
+	else if (type == "Forms2") return new Forms2()
+	.
+	.
+	.
+		else if (type == "FormsN") return new FormsN()
+}
+class User1
+{
+	private FormsSimpleFactory sfo
+	public forms submitForms(string type)
+		{
+			forms myForms = sfo.createForms(type)
+			myForms.saveFormEditor()
+			return myForms
+		}
+}
+.
+.
+.
+class UserN
+{
+	private FormsSimpleFactory sfo
+	public forms submitForms(string type)
+		{
+			forms myForms = sfo.createForms(type)
+			myForms.saveFormEditor()
+			return myForms
+		}
+}
+abstract class forms
+{
+	protected form_id, user_id, is_active: int
+	protected title, description, created_at, updated_at, form_json: string
+	public void saveFormEditor()
+	{ }
+}
+class forms1 extends forms
+{
+	Forms1() //assign user entered values during form creation
+	{
+		form_id = 1
+		user_id = 1
+		is_active = 1
+		title = "title1"
+		description = "description1"
+		created_at = "created_at1"
+		updated_at = "updated_at1"
+		form_json = "form_json1"
+	}
+	public void saveFormEditor()
+	{ }
+}
+.
+.
+.
+class formsN extends forms
+{
+	FormsN() //assign user entered values during form creation
+	{
+		form_id = N
+		user_id = N
+		is_active = N
+		title = "title1"
+		description = "description1"
+		created_at = "created_at1"
+		updated_at = "updated_at1"
+		form_json = "form_json1"
+	}
+	public void saveFormEditor()
+	{ }
+}
+\end{lstlisting}
+
+\clearpage
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.8\textwidth]{FactoryResponses.png}
+        \caption{Responses Class}
+\end{figure}
+
+\begin{lstlisting}
+class ResponsesSimpleFactory
+{
+	public responses createResponses(string type)
+	if (type == "Responses1") return new Responses1()
+	else if (type == "Responses2") return new Responses2()
+	.
+	.
+	.
+		else if (type == "ResponsesN") return new ResponsesN()
+}
+class User1
+{
+	private ResponsesSimpleFactory sfo
+	public responses createResponses(string type)
+	{
+		responses myResponses = sfo.createResponses(type)
+		myResponses.saveResponses()
+		return myResponses
+	}
+}
+.
+.
+.
+class UserN
+{
+	private ResponsesSimpleFactory sfo
+	public responses createResponses(string type)
+	{
+		responses myResponses = sfo.createResponses(type)
+		myResponses.saveResponses()
+		return myResponses
+	}
+}
+abstract class responses
+{
+	protected response_id, form_id, user_id: int
+	protected response_json, created_at, updated_at: string
+	public void saveResponses()
+	{ }
+}
+class Responses1 extends responses
+{
+	Responses1() //assign values entered by the user during response creation
+	{
+		response_id = 1
+		form_id = 1
+		user_id = 1
+		response_json = "response_json1"
+		created_at = "created_at1"
+		updated_at = "updated_at1"
+	}
+	public void saveResponses()
+	{ }	
+}
+.
+.
+.
+class ResponsesN extends responses
+{
+	ResponsesN() //assign values entered by the user during response creation
+	{
+		response_id = N
+		form_id = N
+		user_id = N
+		response_json = "response_jsonN"
+		created_at = "created_atN"
+		updated_at = "updated_atN"
+	}
+	public void saveResponses()
+	{ }	
+}
+\end{lstlisting}
 
@@
 \subsection{Provide the class diagram of the whole system by incorporating the two design patterns.}
+
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=\textwidth]{entireClassDiagram.png}
+        \caption{Whole System Class Diagram}
+\end{figure}
+
 \linebreak
@@
 \subsection{Submit the screenshot of the entire structure of the code within the web framework.}
+
+\singlespacing
+\begin{lstlisting}
+    ├───dLocal
+│   └───dLocal
+│       │   db.sqlite3
+│       │   manage.py
+│       │   models.py
+│       │
+│       ├───CS476P
+│       │   │   asgi.py
+│       │   │   settings.py
+│       │   │   urls.py
+│       │   │   wsgi.py
+│       │   │   __init__.py
+│       │   │
+│       │   └───__pycache__
+│       │           settings.cpython-310.pyc
+│       │           settings.cpython-311.pyc
+│       │           urls.cpython-310.pyc
+│       │           urls.cpython-311.pyc
+│       │           wsgi.cpython-310.pyc
+│       │           wsgi.cpython-311.pyc
+│       │           __init__.cpython-310.pyc
+│       │           __init__.cpython-311.pyc
+│       │
+│       ├───projects
+│       │   │   admin.py
+│       │   │   apps.py
+│       │   │   models.py
+│       │   │   tests.py
+│       │   │   urls.py
+│       │   │   views.py
+│       │   │   __init__.py
+│       │   │
+│       │   ├───migrations
+│       │   │   │   0001_initial.py
+│       │   │   │   0002_tag_project_vote_ratio_project_vote_total_review_and_more.py
+│       │   │   │   0003_form_project_featured_image_response.py
+│       │   │   │   0004_project_owner.py
+│       │   │   │   0005_alter_form_created.py
+│       │   │   │   0005_rename_created_form_created_at_remove_form_id_and_more.py
+│       │   │   │   0006_forms_projectsform.py
+│       │   │   │   0006_rename_created_response_created_at_and_more.py
+│       │   │   │   0007_merge_20230319_1823.py
+│       │   │   │   __init__.py
+│       │   │   │
+│       │   │   └───__pycache__
+│       │   │           0001_initial.cpython-310.pyc
+│       │   │           0001_initial.cpython-311.pyc
+│       │   │           0002_tag_project_vote_ratio_project_vote_total_review_and_more.cpython-310.pyc
+│       │   │           0002_tag_project_vote_ratio_project_vote_total_review_and_more.cpython-311.pyc
+│       │   │           0003_form_project_featured_image_response.cpython-310.pyc
+│       │   │           0003_form_project_featured_image_response.cpython-311.pyc
+│       │   │           0004_project_owner.cpython-310.pyc
+│       │   │           0004_project_owner.cpython-311.pyc
+│       │   │           0005_alter_form_created.cpython-310.pyc
+│       │   │           0005_rename_created_form_created_at_remove_form_id_and_more.cpython-310.pyc
+│       │   │           0006_forms_projectsform.cpython-310.pyc
+│       │   │           0006_rename_created_response_created_at_and_more.cpython-310.pyc
+│       │   │           0007_merge_20230319_1823.cpython-310.pyc
+│       │   │           __init__.cpython-310.pyc
+│       │   │           __init__.cpython-311.pyc
+│       │   │
+│       │   ├───templates
+│       │   │   └───projects
+│       │   │           formEditor.html
+│       │   │           Home.html
+│       │   │           results.html
+│       │   │           saveFormEditor.html
+│       │   │           Survey.html
+│       │   │           Thanks.html
+│       │   │
+│       │   └───__pycache__
+│       │           admin.cpython-310.pyc
+│       │           admin.cpython-311.pyc
+│       │           apps.cpython-310.pyc
+│       │           apps.cpython-311.pyc
+│       │           models.cpython-310.pyc
+│       │           models.cpython-311.pyc
+│       │           urls.cpython-310.pyc
+│       │           urls.cpython-311.pyc
+│       │           views.cpython-310.pyc
+│       │           views.cpython-311.pyc
+│       │           __init__.cpython-310.pyc
+│       │           __init__.cpython-311.pyc
+│       │
+│       ├───static
+│       │   ├───images
+│       │   │   │   default.jpg
+│       │   │   │   logo.png
+│       │   │   │   thankyou.png
+│       │   │   │
+│       │   │   └───profiles
+│       │   │           logo.jpg
+│       │   │           user-default.png
+│       │   │
+│       │   ├───js
+│       │   │       form.js
+│       │   │       manager.js
+│       │   │       survey.js
+│       │   │       userForms.js
+│       │   │
+│       │   └───styles
+│       │           formEditor.css
+│       │           main.css
+│       │           results_table.css
+│       │
+│       ├───staticfiles
+│       │   ├───admin
+│       │   │   ├───css
+│       │   │   │   │   autocomplete.css
+│       │   │   │   │   base.css
+│       │   │   │   │   changelists.css
+│       │   │   │   │   dark_mode.css
+│       │   │   │   │   dashboard.css
+│       │   │   │   │   fonts.css
+│       │   │   │   │   forms.css
+│       │   │   │   │   login.css
+│       │   │   │   │   nav_sidebar.css
+│       │   │   │   │   responsive.css
+│       │   │   │   │   responsive_rtl.css
+│       │   │   │   │   rtl.css
+│       │   │   │   │   widgets.css
+│       │   │   │   │
+│       │   │   │   └───vendor
+│       │   │   │       └───select2
+│       │   │   │               LICENSE-SELECT2.md
+│       │   │   │               select2.css
+│       │   │   │               select2.min.css
+│       │   │   │
+│       │   │   ├───fonts
+│       │   │   │       LICENSE.txt
+│       │   │   │       README.txt
+│       │   │   │       Roboto-Bold-webfont.woff
+│       │   │   │       Roboto-Light-webfont.woff
+│       │   │   │       Roboto-Regular-webfont.woff
+│       │   │   │
+│       │   │   ├───img
+│       │   │   │   │   calendar-icons.svg
+│       │   │   │   │   icon-addlink.svg
+│       │   │   │   │   icon-alert.svg
+│       │   │   │   │   icon-calendar.svg
+│       │   │   │   │   icon-changelink.svg
+│       │   │   │   │   icon-clock.svg
+│       │   │   │   │   icon-deletelink.svg
+│       │   │   │   │   icon-no.svg
+│       │   │   │   │   icon-unknown-alt.svg
+│       │   │   │   │   icon-unknown.svg
+│       │   │   │   │   icon-viewlink.svg
+│       │   │   │   │   icon-yes.svg
+│       │   │   │   │   inline-delete.svg
+│       │   │   │   │   LICENSE
+│       │   │   │   │   README.txt
+│       │   │   │   │   search.svg
+│       │   │   │   │   selector-icons.svg
+│       │   │   │   │   sorting-icons.svg
+│       │   │   │   │   tooltag-add.svg
+│       │   │   │   │   tooltag-arrowright.svg
+│       │   │   │   │
+│       │   │   │   └───gis
+│       │   │   │           move_vertex_off.svg
+│       │   │   │           move_vertex_on.svg
+│       │   │   │
+│       │   │   └───js
+│       │   │       │   actions.js
+│       │   │       │   autocomplete.js
+│       │   │       │   calendar.js
+│       │   │       │   cancel.js
+│       │   │       │   change_form.js
+│       │   │       │   collapse.js
+│       │   │       │   core.js
+│       │   │       │   filters.js
+│       │   │       │   inlines.js
+│       │   │       │   jquery.init.js
+│       │   │       │   nav_sidebar.js
+│       │   │       │   popup_response.js
+│       │   │       │   prepopulate.js
+│       │   │       │   prepopulate_init.js
+│       │   │       │   SelectBox.js
+│       │   │       │   SelectFilter2.js
+│       │   │       │   urlify.js
+│       │   │       │
+│       │   │       ├───admin
+│       │   │       │       DateTimeShortcuts.js
+│       │   │       │       RelatedObjectLookups.js
+│       │   │       │
+│       │   │       └───vendor
+│       │   │           ├───jquery
+│       │   │           │       jquery.js
+│       │   │           │       jquery.min.js
+│       │   │           │       LICENSE.txt
+│       │   │           │
+│       │   │           ├───select2
+│       │   │           │   │   LICENSE.md
+│       │   │           │   │   select2.full.js
+│       │   │           │   │   select2.full.min.js
+│       │   │           │   │
+│       │   │           │   └───i18n
+│       │   │           │           af.js
+│       │   │           │           ar.js
+│       │   │           │           az.js
+│       │   │           │           bg.js
+│       │   │           │           bn.js
+│       │   │           │           bs.js
+│       │   │           │           ca.js
+│       │   │           │           cs.js
+│       │   │           │           da.js
+│       │   │           │           de.js
+│       │   │           │           dsb.js
+│       │   │           │           el.js
+│       │   │           │           en.js
+│       │   │           │           es.js
+│       │   │           │           et.js
+│       │   │           │           eu.js
+│       │   │           │           fa.js
+│       │   │           │           fi.js
+│       │   │           │           fr.js
+│       │   │           │           gl.js
+│       │   │           │           he.js
+│       │   │           │           hi.js
+│       │   │           │           hr.js
+│       │   │           │           hsb.js
+│       │   │           │           hu.js
+│       │   │           │           hy.js
+│       │   │           │           id.js
+│       │   │           │           is.js
+│       │   │           │           it.js
+│       │   │           │           ja.js
+│       │   │           │           ka.js
+│       │   │           │           km.js
+│       │   │           │           ko.js
+│       │   │           │           lt.js
+│       │   │           │           lv.js
+│       │   │           │           mk.js
+│       │   │           │           ms.js
+│       │   │           │           nb.js
+│       │   │           │           ne.js
+│       │   │           │           nl.js
+│       │   │           │           pl.js
+│       │   │           │           ps.js
+│       │   │           │           pt-BR.js
+│       │   │           │           pt.js
+│       │   │           │           ro.js
+│       │   │           │           ru.js
+│       │   │           │           sk.js
+│       │   │           │           sl.js
+│       │   │           │           sq.js
+│       │   │           │           sr-Cyrl.js
+│       │   │           │           sr.js
+│       │   │           │           sv.js
+│       │   │           │           th.js
+│       │   │           │           tk.js
+│       │   │           │           tr.js
+│       │   │           │           uk.js
+│       │   │           │           vi.js
+│       │   │           │           zh-CN.js
+│       │   │           │           zh-TW.js
+│       │   │           │
+│       │   │           └───xregexp
+│       │   │                   LICENSE.txt
+│       │   │                   xregexp.js
+│       │   │                   xregexp.min.js
+│       │   │
+│       │   ├───images
+│       │   │   │   default.jpg
+│       │   │   │   logo.png
+│       │   │   │   thankyou.png
+│       │   │   │
+│       │   │   └───profiles
+│       │   │           logo.jpg
+│       │   │           user-default.png
+│       │   │
+│       │   ├───js
+│       │   │       form.js
+│       │   │       manager.js
+│       │   │       survey.js
+│       │   │
+│       │   └───styles
+│       │           formEditor.css
+│       │           main.css
+│       │           results_table.css
+│       │
+│       ├───templates
+│       │       file.vuerd.json
+│       │       main.html
+│       │       navbar.html
+│       │
+│       └───users
+│           │   admin.py
+│           │   apps.py
+│           │   forms.py
+│           │   models.py
+│           │   tests.py
+│           │   urls.py
+│           │   views.py
+│           │   __init__.py
+│           │
+│           ├───migrations
+│           │   │   0001_initial.py
+│           │   │   0002_profile_username.py
+│           │   │   0003_profile_location_skill.py
+│           │   │   __init__.py
+│           │   │
+│           │   └───__pycache__
+│           │           0001_initial.cpython-310.pyc
+│           │           0001_initial.cpython-311.pyc
+│           │           0002_profile_username.cpython-310.pyc
+│           │           0002_profile_username.cpython-311.pyc
+│           │           0003_profile_location_skill.cpython-310.pyc
+│           │           0003_profile_location_skill.cpython-311.pyc
+│           │           __init__.cpython-310.pyc
+│           │           __init__.cpython-311.pyc
+│           │
+│           ├───templates
+│           │   └───users
+│           │           formEditor-old.html
+│           │           login_register.html
+│           │           profiles.html
+│           │
+│           └───__pycache__
+│                   admin.cpython-310.pyc
+│                   admin.cpython-311.pyc
+│                   apps.cpython-310.pyc
+│                   apps.cpython-311.pyc
+│                   forms.cpython-310.pyc
+│                   forms.cpython-311.pyc
+│                   models.cpython-310.pyc
+│                   models.cpython-311.pyc
+│                   urls.cpython-310.pyc
+│                   urls.cpython-311.pyc
+│                   views.cpython-310.pyc
+│                   views.cpython-311.pyc
+│                   __init__.cpython-310.pyc
+│                   __init__.cpython-311.pyc
+│
+└───formEditorJS
+        form.js
+        index.html
+\end{lstlisting}
+
+\doublespacing
+
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.45\textwidth]{5a1.png}
+        %\caption{Forms Class in Users Application and Project Application}
+\end{figure}
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.45\textwidth]{5a2.png}
+        %\caption{Forms Class in Users Application and Project Application}
+\end{figure}
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.45\textwidth]{5a3.png}
+        %\caption{Forms Class in Users Application and Project Application}
+\end{figure}
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.45\textwidth]{5a4.png}
+        %\caption{Forms Class in Users Application and Project Application}
+\end{figure}
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.45\textwidth]{5a5.png}
+        %\caption{Forms Class in Users Application and Project Application}
+\end{figure}
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.45\textwidth]{5a6.png}
+        %\caption{Forms Class in Users Application and Project Application}
+\end{figure}
+
 \linebreak
     \hfill \break
+    \clearpage
+\subsection{Deployment diagram regarding the hardware configuration of the code. Indicate the supported Web browsers, the application/Web servers and the database solution.}
 
-\subsection{Deployment diagram regarding the hardware configuration of the code. Indicate the supported Web browsers, the application/Web servers and the database solution.}
+All web browsers are supported. Our application is created using the Django framework and the web server is ngrok. MySQL was used as the database solution.
+
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.9\textwidth]{deploymentDiagram.png}
+        %\caption{Forms Class in Users Application and Project Application}
+\end{figure}
+
 \linebreak
-    \hfill \break
+\clearpage    
+\subsection{Screenshots of all table contents of the system data.}
 
-\subsection{Screenshots of all table contents of the system data.}
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.95\textwidth]{5c1.png}
+\end{figure}
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.95\textwidth]{5c2.png}
+\end{figure}
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.95\textwidth]{5c3.png}
+\end{figure}
+\newpage
+
 \linebreak
-    \hfill \break
-
 \subsection{GitHub link of the entire program.
@@
 \subsection{Correctness testing using four test cases (screenshots of both inputs and outputs).}
-\newline
+%\newline
 
@@
     \item[] Input: Feedback gatherer creates a survey by selecting the types of answers and entering the questions. 
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{correct1.png}
+        %\caption{Profile Class}
+\end{figure}
 
 Output: When they click the “Create Survey” button, a QR code is generated.
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{correct2.png}
+        %\caption{Profile Class}
+\end{figure}
 
 Input: Feedback gatherer clicks on one of the past surveys.
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{correct3.png}
+        %\caption{Profile Class}
+\end{figure}
 
 Output: Feedback gatherer can view the responses to the correct survey.
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{correct4.png}
+        %\caption{Profile Class}
+\end{figure}
 \end{itemize}
@@
 \hfill \break
+\clearpage
 \textbf{Respondent:}
@@
     \item[] Input: Respondent scans the QR code.
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{correct5.png}
+        %\caption{Profile Class}
+\end{figure}
+
     \item[] Output: Respondent is taken to the correct survey.
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{correct6.png}
+        %\caption{Profile Class}
+\end{figure}
+\clearpage
     \item[] Input: Respondent completes the survey and clicks submit.
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{correct7.png}
+        %\caption{Profile Class}
+\end{figure}
+
     \item[] Output: Respondent is taken to the thank you page.
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{correct8.png}
+        %\caption{Profile Class}
+\end{figure}
 \end{itemize}
@@
     \item[] Input: Feedback gatherer tries to go to the sign up page while already logged in.
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{robust1.png}
+        %\caption{Profile Class}
+\end{figure}
+\item[]
 
 Output: Feedback gatherer is redirected to landing page.
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{robust2.png}
+        %\caption{Profile Class}
+\end{figure}
 
 Input: Feedback gatherer tries to go to the login page while already logged in.
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{robust3.png}
+        %\caption{Profile Class}
+\end{figure}
+\clearpage
+Output: Feedback gatherer is redirected to landing page.
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{robust4.png}
+        %\caption{Profile Class}
+\end{figure}
 
-Output: Feedback gatherer is redirected to landing page.
 \end{itemize}
@@
     \item[] Input: Respondent tries to go the landing page while not logged in.
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{robust5.png}
+        %\caption{Profile Class}
+\end{figure}
 
 Output: Respondent is redirected to login page.
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{robust6.png}
+        %\caption{Profile Class}
+\end{figure}
 
 Input: Respondent tries to go the create survey page while not logged in.
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{robust7.png}
+        %\caption{Profile Class}
+\end{figure}
 
 Output: Respondent is redirected to login page.
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{robust8.png}
+        %\caption{Profile Class}
+\end{figure}
 
@@
 \begin{itemize}
-    \item[] Create survey: Time taken for the survey data to be stored in the database and the QR code to be generated.
+    \item[] Create survey: Time taken for the survey data to be stored in the database and the QR code to be generated. \(\sim \)300ms
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{time1.png}
+        %\caption{Profile Class}
+\end{figure}
 
-View responses: Time taken for the response data to be shown to the feedback gatherer after clicking a past survey.
+View responses: Time taken for the response data to be shown to the feedback gatherer after clicking a past survey. \(\sim \)320ms
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{time2.png}
+        %\caption{Profile Class}
+\end{figure}
 \end{itemize}
@@
 
+\clearpage
 \textbf{Respondent:}
 \begin{itemize}
-    \item[] Go to survey: Time taken for the survey to be loaded from the database when the QR code is scanned.
+    \item[] Go to survey: Time taken for the survey to be loaded from the database when the QR code is scanned. \(\sim \)600ms
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{time3.png}
+        %\caption{Profile Class}
+\end{figure}
 
-Submit responses: Time taken for the response data to be stored in the database and to show the respondent that the responses were successfully submitted.
+Submit responses: Time taken for the response data to be stored in the database and to show the respondent that the responses were successfully submitted. \(\sim \)125ms
+\begin{figure}[h]
+        \centering
+        \includegraphics[width=0.6\textwidth]{time4.png}
+        %\caption{Profile Class}
+\end{figure}
 
@@
 \hfill \break
-Method: Use inspect network in Google Chrome.
+Method: Network tab on Google Chrome inspect.
 

### 2023-03-21 src/index.js
Delete index.js

@@ -1,41 +1,0 @@
-import ReactDOM from "react-dom";
-import { BrowserRouter, Routes, Route } from "react-router-dom";
-
-import Layout from "./Layout";
-import Home from "./pages/Home";
-import Signup from "./pages/Signup";
-import Login from "./pages/Login";
-import LandingPage from "./pages/LandingPage";
-import Profile from "./pages/Profile";
-import QRcode from "./pages/QRcode";
-import Survey from "./pages/Survey";
-import Thanks from "./pages/Thanks";
-//import dbtest from "./pages/dbtest";
-import './main.css';
-
-/*
-import { Amplify } from 'aws-amplify';
-import config from './aws-exports';
-Amplify.configure(config);*/
-
-export default function App() {
-  return (
-    <BrowserRouter>
-      <Routes>
-        <Route path="/" element={<Layout />}>
-          <Route index element={<Home />} />
-          <Route path="Signup" element={<Signup />} />
-          <Route path="Login" element={<Login />} />
-          <Route path="LandingPage" element={<LandingPage />} />
-          <Route path="Profile" element={<Profile />} />
-          <Route path="QRcode" element={<QRcode />} />
-          <Route path="Survey" element={<Survey />} />
-          <Route path="Thanks" element={<Thanks />} />
-          {/* <Route path="dbtest" element={<dbtest />} /> */}
-        </Route>
-      </Routes>
-    </BrowserRouter>
-  );
-}
-
-ReactDOM.render(<App />, document.getElementById("root"));

### 2023-03-21 src/Layout.js
Delete Layout.js

@@ -1,16 +1,0 @@
-import React from "react";
-import {Outlet} from "react-router-dom";
-import Header from "./Header";
-import Footer from "./Footer";
-
-const Layout = () => {
-  return (
-    <>
-      <Header />
-      <Outlet />
-      <Footer />
-    </>
-  );
-};
-
-export default Layout;

### 2023-03-21 src/Header.js
Delete Header.js

@@ -1,12 +1,0 @@
-import React from "react";
-
-function Header() {
-  return (
-    <nav>
-      <div class="logo"></div>
-      <h1>CommentCorner</h1>
-    </nav>
-  );
-}
-
-export default Header;

### 2023-03-21 src/Footer.js
Delete Footer.js

@@ -1,11 +1,0 @@
-import React from "react";
-
-function Footer() {
-  return (
-    <footer id="footer">
-      <p>Team members: Zachary, John, Payton, Liam, Genevieve </p>
-    </footer>
-  );
-}
-
-export default Footer;

### 2023-03-21 src/App.js
Delete App.js

@@ -1,25 +1,0 @@
-import logo from "./logo.svg";
-import "@aws-amplify/ui-react/styles.css";
-
-import {
-  withAuthenticator,
-  Button,
-  Heading,
-  Image,
-  View,
-  Card,
-} from "@aws-amplify/ui-react";
-
-function App({ signOut }) {
-  return (
-    <View className="App">
-      <Card>
-        <Image src={logo} className="App-logo" alt="logo" />
-        <Heading level={1}>We now have Auth!</Heading>
-      </Card>
-      <Button onClick={signOut}>Sign Out</Button>
-    </View>
-  );
-}
-
-export default withAuthenticator(App);

### 2023-03-21 src/pages/CreateSurvey.js
Delete CreateSurvey.js

@@ -1,9 +1,0 @@
-
-function CreateSurvey() {
-    return (
-        <div >
-        </div>
-    );
-  }
-  
-  export default CreateSurvey;

### 2023-03-21 src/pages/Home.js
Delete Home.js

@@ -1,12 +1,0 @@
-import { Link } from "react-router-dom";
-
-function Home() {
-    return (
-        <div>
-            <h1>this is where the home page will go</h1>
-            <Link to="/login">log in.</Link>
-        </div>
-    );
-  }
-  
-  export default Home;

### 2023-03-21 src/pages/LandingPage.js
Delete LandingPage.js

@@ -1,22 +1,0 @@
-
-function LandingPage() {
-    return (
-        <div>
-        <h2>Hello fname!</h2>
-    
-        <a href="{% url 'landingpage' %}">+ Create New Survey</a>
-            <div>
-                <div class="dropdown">
-                    survey name
-                    <b class="dropbtn"> &#x22EE;</b>
-                    <div class="dropdown-content">
-                      <a href="#">Delete</a>
-                      <a href="#">Get QR</a>
-                    </div>
-                  </div>
-            </div>
-      </div>
-    );
-  }
-  
-  export default LandingPage;

### 2023-03-21 src/pages/Login.js
Delete Login.js

@@ -1,40 +1,0 @@
-import { Link } from "react-router-dom";
-
-function Login() {
-    return (
-        <div class="auth">
-
-    <div class="card">
-
-      <div class="auth__header text-center">
-        <h2>Account Login</h2>
-      </div>
-
-
-      <form  method = "POST" class="form auth__form">
-
-        <div class="form__field">
-          <input class="input input--text" id="formInput#text" type="text" name="username"
-            placeholder="Email" />
-        </div>
-
-        <div class="form__field">
-          <input class="input input--password" id="formInput#passowrd" type="password" name="password"
-            placeholder="Password" />
-        </div>
-        <div class="auth__actions">
-          <input class="btn btn--sub btn--lg" type="submit" value="Login" />
-        </div>
-        <div class="auth__alternative">
-          <p>Don’t have an Account?</p>
-          <a href="">Sign Up</a>
-        </div>
-
-      </form>
-    </div>
-  </div>
-
-    );
-  }
-  
-  export default Login;

### 2023-03-21 src/pages/Profile.js
Delete Profile.js

@@ -1,9 +1,0 @@
-
-function Profile() {
-    return (
-        <div >
-        </div>
-    );
-  }
-  
-  export default Profile;

### 2023-03-21 src/pages/QRcode.js
Delete QRcode.js

@@ -1,17 +1,0 @@
-
-function QRcode() {
-    return (
-        <div>
-    <h2>Survey Name:</h2>
-
-    <div>
-        <img id='barcode' src="https://api.qrserver.com/v1/create-qr-code/?data=HelloWorld&amp;size=150x150" alt="" width="150" height="150" />
-    </div>
-    
-    <a href="{% url 'landingpage' %}">Back to landing</a>
-
-  </div>
-    );
-  }
-  
-  export default QRcode;

### 2023-03-21 src/pages/Signup.js
Delete Signup.js

@@ -1,45 +1,0 @@
-
-function Signup() {
-    return (
-        <div class="auth">
-
-        <div class="card">
-    
-          <div class="auth__header text-center">
-            <h2>Sign up</h2>
-          </div>
-          
-          <form action="{% url 'signup' %}" method = "POST" class="form auth__form">
-
-            <div class="form__field">
-              <input class="input input--text" id="formInput#text" type="text" name="fname"
-                placeholder="First name" />
-            </div>
-    
-            <div class="form__field">
-                <input class="input input--text" id="formInput#text" type="text" name="lname"
-                  placeholder="Last name" />
-            </div>
-    
-            <div class="form__field">
-                <input class="input input--text" id="formInput#text" type="text" name="username"
-                  placeholder="Email" />
-            </div>
-    
-              <div class="form__field">
-                <input class="input input--password" id="formInput#passowrd" type="password" name="password"
-                  placeholder="Password" />
-              </div>
-    
-            <div class="auth__actions">
-              <input class="btn btn--sub btn--lg" type="submit" value="Sign up" />
-            </div>
-    
-          </form>
-          
-        </div>
-      </div>
-    );
-  }
-
-export default Signup;

### 2023-03-21 src/pages/Survey.js
Delete Survey.js

@@ -1,9 +1,0 @@
-
-function Survey() {
-    return (
-        <div >
-        </div>
-    );
-  }
-  
-  export default Survey;

### 2023-03-21 src/pages/Thanks.js
Delete Thanks.js

@@ -1,12 +1,0 @@
-import { Link } from "react-router-dom";
-
-function Thanks() {
-    return (
-        <div >
-            <img src="http://clipart-library.com/image_gallery2/Thank-You-PNG-Image.png" width="313" length="391"/>
-            <p><Link to="/">Create your own server</Link></p>
-        </div>
-    );
-  }
-  
-  export default Thanks;

### 2023-03-21 src/pages/dbtest.js
Delete dbtest.js

@@ -1,25 +1,0 @@
-const express = require('express');
-const db = require('../config/db');
-const cors = require('cors')
-
-const app = express();
-const  PORT = 3002;
-app.use(cors());
-app.use(express.json())
-
-
-app.get("/api/get", (req,res)=>{
-db.query("SELECT * FROM users", (err,result)=>{
-    if(err) {
-    console.log(err)
-    } 
-res.send(result)
-});   });
-
-
-app.listen(PORT, ()=>{
-    console.log(`Server is running on ＄{PORT}`)
-})
-
-
-export default dbtest;
